---
title: "PipPenn Data Analysis"
author: "Quy Cao, Haochang Shou, Virgilio Gonzenbach"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center",
                      message = FALSE, warning = FALSE,
                      fig.width = 10)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

options(scipen=999)


library(corrplot)
library(caret)
library(ROCR)
library(dygraphs)
library(xts)
library(lubridate)
library(ggplot2)
library(zoo)
library("factoextra") ## plot pcs
library(kernlab)      # SVM methodology
library(e1071)        # SVM methodology
library(Movelet)
library(dplyr)
library(stringr)
```

## Exploration of the Time Series Data

Currently we have data from 10 subjects. Here we only show the examples from Patient 52.

```{r load,echo=FALSE}

#Load Data
#dat<-read.csv('/Users/hshou/Box/PipPenn/Data/patient52.csv',header = TRUE,stringsAsFactors = FALSE)
dat<-read.csv('Data/patient52.csv', header = TRUE,stringsAsFactors = FALSE)

#convert time series
convertTimeSeries = function(df){
  
  makeNumericTime = function(){
    timestamp <- substr(df$activity_timestamp,12,23)
    time<-as.numeric(hms(timestamp))
    time<- time-time[1]
    return(time)
  }
  
  df$time = makeNumericTime()
  
  # Convert activity name to numeric label
  df$Activitylabel <- match(df$ActivityName,
                            unique(df$ActivityName))
  
  return(df)
}

dat = convertTimeSeries(dat)
dat$Wrist_Location = gsub(" ", "", dat$Wrist_Location, fixed = TRUE) %>% factor()
```  

The code for activity types are 

```{r actname,echo=FALSE}
data.frame(Label = 1:length(unique(dat$ActivityName)), Name= unique(dat$ActivityName))
```


```{r plot, echo=FALSE}
plotTimeSeries = function(df, vars=c("accel", "rotate", "attitude", "gravity", "magneto"), wrist = "right", plotLabel=TRUE){
  
  if(plotLabel){
    df = df %>% filter(Wrist_Location == wrist) %>% select(time, starts_with(vars), Activitylabel)
  }else{
    df = df %>% filter(Wrist_Location == wrist) %>% select(time, starts_with(vars))
  }
  df %>% dygraph(main=paste('Patient', df$PatientID[1], str_to_title(vars), str_to_title(wrist),'Wrist')) %>% 
    dyAxis("x", drawGrid = FALSE) %>%
    dyOptions(colors = RColorBrewer::brewer.pal(7, "Set1")) %>%
    dyRangeSelector()
}

plotTimeSeries(dat, "accel", "right")
plotTimeSeries(dat, "rotate", "right")
plotTimeSeries(dat, "attitude", "right")
plotTimeSeries(dat, "gravity", "right")
plotTimeSeries(dat, "magneto", "right")
```

Consider "8.Med taking" chunk of activities for analysis.

```{r,eval=FALSE}
## select 8.Med taking
med_taking_8 <- subset(dat, Activitylabel == 16)
#dim(med_taking_8)
#min(med_taking_8$time)

# padding around activity
med_taking_8$mini_activity <- factor(ifelse(med_taking_8$time > (min(med_taking_8$time)+2)
                                            & med_taking_8$time < (min(med_taking_8$time)+4),
                                            "Open Bottle","Others"), levels = c("Others","Open Bottle"))
## check mini activity
table(med_taking_8$mini_activity)

plotTimeSeries(med_taking_8, "accel", plotLabel = FALSE)

## check correlation
corrplot(cor(med_taking_8[,c("accel_x_coord","accel_y_coord","accel_z_coord",
                         "rotate_x_coord","rotate_y_coord", "rotate_z_coord")]))

## talk about this with Haochang
plot(med_taking_8$time,med_taking_8$accel_x_coord, type = "l")
lines(rollmean(med_taking_8$accel_x_coord, k = 3), col = "red")
lines(lowess(med_taking_8$time,med_taking_8$accel_x_coord, f = 0.000001), col = "green") 
legend("topleft",                                               # Add legend to line plot
       col = c("red", "green"),
       lty = 1,
       lwd = 2,
       cex = 0.5,
       c("Moving Average, k = 3", "Lowess Smooth, f = 0.000001"))

## fit logistic model
glm_open_bottle <- glm(mini_activity ~ accel_x_coord + accel_y_coord + accel_z_coord +
                         rotate_x_coord + rotate_y_coord + rotate_z_coord + DeviceName,
                         family = "binomial", data = med_taking_8)
summary(glm_open_bottle)
pscl::pR2(glm_open_bottle)

#### perform PCA on 3 accel and 3 rotate variables
predictors <- med_taking_8[,c("accel_x_coord","accel_y_coord","accel_z_coord",
                              "rotate_x_coord","rotate_y_coord", "rotate_z_coord")]
predictors.pca <- prcomp(predictors, center=TRUE, scale.=TRUE)
summary(predictors.pca)
pcs <- predictors.pca$x ## the PCs for regression

## check pc plots
fviz_pca_var(predictors.pca,axes = c(1, 2))
fviz_pca_var(predictors.pca,axes = c(3, 4))
fviz_pca_var(predictors.pca,axes = c(5, 6))

## combine pcs to df
med_taking_8 <- cbind(med_taking_8,pcs)

## perform PCR
glm_pcr <- glm(mini_activity ~ PC1 + PC2 + PC3 + DeviceName, family = "binomial", data = med_taking_8)
summary(glm_pcr)
pscl::pR2(glm_pcr)

#### SVM
svm.df <- med_taking_8[, c("mini_activity","accel_x_coord","accel_y_coord","accel_z_coord",
                           "rotate_x_coord","rotate_y_coord", "rotate_z_coord")]
## find optimal cost of misclassification
# tune.out <- tune(svm, mini_activity ~ .,
#                  data = svm.df,
#                  kernel = "polynomial",
#                  ranges = list(cost = c(0.001, 0.01, 0.1, 1, 5, 10)) 
#                  ) # cost = 1
# ## extract the best model
# (bestmod <- tune.out$best.model)

## Fit Support Vector Machine model to data set
svmfit <- svm(mini_activity ~ ., data = svm.df, kernel = "polynomial", cost = 1)
summary(svmfit)
## Create a table of misclassified observations
(misclass <- table(predict = svmfit$fitted, truth = svm.df$mini_activity)) ## NOPE
```

I also study the movelet package. Thanks to Jiawei example, I was able to put together a workflow and this is what I got:

STEP 1: create an AcceleData using the *Acceleration_Create*

STEP 2: create chapters of movelets from the AcceleData above using *Movelet_Create*. Now you have your reference chapters. Next step is prediction of unlabeled chapters

STEP 3: Predict label for each unlabeled chapter of movelets using *Movelet_Pred*

STEP 4: Validate results using *Movelet_Validation*

Example:

```{r, eval = FALSE}
data.Sample5 <- Acceleration_Create("Data/data_label.csv",subjectName="Sample5",frequency=30)
Ch.sedentary_act.Sample5 <- Movelet_Create(5701,5761,data.Sample5, "sedentary_act")
pred <- Movelet_Pred(data.Sample5,Act.Names=c("sedentary_act"),vote=TRUE)
validation <- Movelet_Validation(data.Sample5, Prediction = pred, Act.Names=c("sedentary_act"))
```

## Try movelet with patient 52

<!-- ### Using 3 accel variables -->

```{r,eval=FALSE, echo = FALSE}
movelet.dat <- dat[,c("accel_x_coord","accel_y_coord","accel_z_coord","ActivityName","Wrist_Location")]
#movelet.dat <- dat[,c("rotate_x_coord","rotate_y_coord","rotate_z_coord","ActivityName","Wrist_Location")]
movelet.dat$ActivityName <- gsub(" ", "_", movelet.dat$ActivityName)

## select right wrist
movelet.dat.right <- subset(movelet.dat, Wrist_Location =="right     ")

## create accel data 
patient.52 <- Acceleration_Create(movelet.dat.right,subjectName="patient52",frequency=300) #3 variables * 100 hz
#print.AcceleData(patient.52)

## Train Open_Water_Bottle_and_Take_a_Drink chapter
from <- min(which(patient.52$Label == "Open_Water_Bottle_and_Take_a_Drink"))
to <- max(which(patient.52$Label == "Open_Water_Bottle_and_Take_a_Drink"))
Ch.Open_Water_Bottle_and_Take_a_Drink.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                                                  DATA = patient.52, 
                                                      ChapName = "Open_Water_Bottle_and_Take_a_Drink")
## Train walk chapter
from <- min(which(patient.52$Label == "Walk"))
to <- max(which(patient.52$Label == "Walk"))
Ch.Walk.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Walk")
## Train Pour_Water_into_a_Cup chapter
from <- min(which(patient.52$Label == "Pour_Water_into_a_Cup"))
to <- max(which(patient.52$Label == "Pour_Water_into_a_Cup"))
Ch.Pour_Water_into_a_Cup.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Pour_Water_into_a_Cup")
## train Look_around_in_bag_or_purse chapter
from <- min(which(patient.52$Label == "Look_around_in_bag_or_purse"))
to <- max(which(patient.52$Label == "Look_around_in_bag_or_purse"))
Ch.Look_around_in_bag_or_purse.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Look_around_in_bag_or_purse")
## train eat from bag chapter
from <- min(which(patient.52$Label == "Eat_From_Bag"))
to <- max(which(patient.52$Label == "Eat_From_Bag"))
Ch.Eat_From_Bag.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Eat_From_Bag")

## train open water bottle chapter
from <- min(which(patient.52$Label == "9._Med_Taking")) + 100 ## 12:11:39 picks up water bottle to uncap
to <- max(which(patient.52$Label == "9._Med_Taking")) + 300 ## 12:11:41 returns opened water bottle to table
Ch.Open_water_bottle.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Open_water_bottle")

## train pick up and open a pill bottle chapter
from <- min(which(patient.52$Label == "9._Med_Taking")) + 400 ## 12:11:42 picks up pill bottle
to <- max(which(patient.52$Label == "9._Med_Taking")) + 800 ## 112:11:46 pours pill out into left hand
Ch.Pick_up_and_open_a_pill_bottle.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Pick_up_and_open_a_pill_bottle")
## train pour pill chapter
from <- min(which(patient.52$Label == "9._Med_Taking")) + 800 ## 12:11:46
to <- max(which(patient.52$Label == "9._Med_Taking")) + 900 ## 12:11:47
Ch.Pour_pill.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Pour_pill")

## train take pill chapter 
from <- min(which(patient.52$Label == "9._Med_Taking")) + 900 ## 12:11:47 
to <- max(which(patient.52$Label == "9._Med_Taking")) + 1000 ## 112:11:48
Ch.Take_pill.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Take_pill")

## train Wash_Hands chapter
from <- min(which(patient.52$Label == "Wash_Hands"))
to <- max(which(patient.52$Label == "Wash_Hands"))
Ch.Wash_Hands.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Wash_Hands")

## test data
test.dat <- subset(movelet.dat, ActivityName %in% c("Turn_Key","Open_Door","6._Med_Taking","7._Med_Taking") & Wrist_Location =="right     ")
test.dat.patient.52 <- Acceleration_Create(test.dat,subjectName="patient52",frequency=300) #3 variables * 100 hz

time.test<- as.numeric(row.names(test.dat))
  
#pred <- Movelet_Pred(test.dat.patient.52, Act.Names=c("Open_water_bottle","Pick_up_and_open_a_pill_bottle","Pour_pill","Take_pill","Eat_From_Bag"), vote=TRUE)

train.label=c( "Open_water_bottle","Pick_up_and_open_a_pill_bottle","Pour_pill","Take_pill","Eat_From_Bag","Pour_Water_into_a_Cup",'Walk','Wash_Hands','Look_around_in_bag_or_purse')

#expand the prediction activity labels to include all trained chapters
#pred <- Movelet_Pred(test.dat.patient.52, Act.Names=train.label, vote=TRUE)
# Save it
#saveRDS(pred, file = "patient52_3accels_pred.rds")
# load it
patient52_3accels_pred <- readRDS(file = "patient52_3accels_pred.rds")
#names(patient52_3accels_pred$Pred)
##plot the trained vs. observed labels
# dygraph(data=c(dat[time.test,c('time',names(dat)[c(11:13,30)])],pred$Pred),main=paste('Patient', dat$PatientID[1],' Rotation Right Wrist',sep=''))%>% 
#   dyAxis("x", drawGrid = FALSE) %>%
#   dyOptions(colors = RColorBrewer::brewer.pal(7, "Set1"))  %>%
#   dyRangeSelector()


table(patient52_3accels_pred$Pred)
#dim(test.dat)

time <- seq(1,length(patient52_3accels_pred$Pred))
plot(x = patient52_3accels_pred$Pred , y = time, xlab = "Prediction", ylab = "Time", xaxt = "n", pch = 20)
axis(1, at=seq(1,length(train.label)), labels= FALSE)
text(seq(1,length(train.label)),par("usr")[3] - 100, labels = train.label, srt = 45, xpd = TRUE, cex = 0.5, adj = c(1,0))
text(x = 1.5, y = 90, "Open_Door", cex = 0.5)
abline(h = max(which(test.dat$ActivityName == "Open_Door")), col="red")
text(x = 1.5, y = 300, "Turn_Key", cex = 0.5)
abline(h = max(which(test.dat$ActivityName == "Turn_Key")), col="red")
text(x = 1.5, y = 600, "Pick_up_and_open_a_pill_bottle", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 400), col="red")
text(x = 1.5, y = 920, "Take_pill", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 500), col="red")
text(x = 1.5, y = 1080, "Drink_water", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 650), col="red")
text(x = 1.5, y = 1300, "Pick_up_and_open_a_water_bottle_and_put_it_down", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "7._Med_Taking") + 250), col="red")
text(x = 1.5, y = 1900, "Pick_up_and_open_a_pill_bottle_and_take_pill", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "7._Med_Taking") + 650), col="red")
text(x = 1.5, y = 2100, "Drink_water", cex = 0.5)


# abline(v=100, col="blue") ## pick up and open water bottle
# abline(v=500, col="blue") ## pick up and open pill bottle
# abline(v=900, col="blue") ## pour pill 
# abline(v=1200, col="blue") ## take pill 
# abline(v=1300, col="blue") ## pick water bottle and drink  
# abline(v=1600, col="blue") ## end
# text(x = 300, y = 4, "pick/open water bottle", cex = 0.5)
# text(x = 700, y = 4, "pick/open pill bottle", cex = 0.5)
# text(x = 1000, y = 4, "pour pill", cex = 0.5)
# text(x = 1250, y = 4, "take pill", cex = 0.5)
# text(x = 1500, y = 4, "pick/drink water bottle", cex = 0.5)


# table(pred$Pred) # 1 = Open_a_pill_bottle_and_take_a_pilll; 3= Wash_Hands
# 
#    1    3 
# 2130 3136 
# > length(pred$Pred)
# [1] 5266
# > length(which(patient.52$Label=="8._Med_Taking"))
# [1] 2281
# > length(which(patient.52$Label=="Wash_Hands"))
# [1] 3284

#validation <- Movelet_Validation(test.dat.patient.52, Prediction = pred$Pred, Act.Names = c("Walk","Open_Water_Bottle_and_Take_a_Drink"))

```

<!-- ### Using 3 rotation variables -->

```{r,eval=FALSE, echo = FALSE}
#movelet.dat <- dat[,c("accel_x_coord","accel_y_coord","accel_z_coord","ActivityName")]
movelet.dat <- dat[,c("rotate_x_coord","rotate_y_coord","rotate_z_coord","ActivityName","Wrist_Location")]
movelet.dat$ActivityName <- gsub(" ", "_", movelet.dat$ActivityName)

## select right wrist
movelet.dat.right <- subset(movelet.dat, Wrist_Location =="right     ")

## create accel data 
patient.52 <- Acceleration_Create(movelet.dat.right,subjectName="patient52",frequency=300) #3 variables * 100 hz
#print.AcceleData(patient.52)

## Train Open_Water_Bottle_and_Take_a_Drink chapter
from <- min(which(patient.52$Label == "Open_Water_Bottle_and_Take_a_Drink"))
to <- max(which(patient.52$Label == "Open_Water_Bottle_and_Take_a_Drink"))
Ch.Open_Water_Bottle_and_Take_a_Drink.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                                                  DATA = patient.52, 
                                                      ChapName = "Open_Water_Bottle_and_Take_a_Drink")
## Train walk chapter
from <- min(which(patient.52$Label == "Walk"))
to <- max(which(patient.52$Label == "Walk"))
Ch.Walk.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Walk")
## Train Pour_Water_into_a_Cup chapter
from <- min(which(patient.52$Label == "Pour_Water_into_a_Cup"))
to <- max(which(patient.52$Label == "Pour_Water_into_a_Cup"))
Ch.Pour_Water_into_a_Cup.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Pour_Water_into_a_Cup")
## train Look_around_in_bag_or_purse chapter
from <- min(which(patient.52$Label == "Look_around_in_bag_or_purse"))
to <- max(which(patient.52$Label == "Look_around_in_bag_or_purse"))
Ch.Look_around_in_bag_or_purse.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Look_around_in_bag_or_purse")
## train eat from bag chapter
from <- min(which(patient.52$Label == "Eat_From_Bag"))
to <- max(which(patient.52$Label == "Eat_From_Bag"))
Ch.Eat_From_Bag.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Eat_From_Bag")

## train open water bottle chapter
from <- min(which(patient.52$Label == "9._Med_Taking")) + 100 ## 12:11:39 picks up water bottle to uncap
to <- max(which(patient.52$Label == "9._Med_Taking")) + 300 ## 12:11:41 returns opened water bottle to table
Ch.Open_water_bottle.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Open_water_bottle")

## train pick up and open a pill bottle chapter
from <- min(which(patient.52$Label == "9._Med_Taking")) + 400 ## 12:11:42 picks up pill bottle
to <- max(which(patient.52$Label == "9._Med_Taking")) + 800 ## 112:11:46 pours pill out into left hand
Ch.Pick_up_and_open_a_pill_bottle.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Pick_up_and_open_a_pill_bottle")
## train pour pill chapter
from <- min(which(patient.52$Label == "9._Med_Taking")) + 800 ## 12:11:46
to <- max(which(patient.52$Label == "9._Med_Taking")) + 900 ## 12:11:47
Ch.Pour_pill.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Pour_pill")

## train take pill chapter 
from <- min(which(patient.52$Label == "9._Med_Taking")) + 900 ## 12:11:47 
to <- max(which(patient.52$Label == "9._Med_Taking")) + 1000 ## 112:11:48
Ch.Take_pill.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Take_pill")

## train Wash_Hands chapter
from <- min(which(patient.52$Label == "Wash_Hands"))
to <- max(which(patient.52$Label == "Wash_Hands"))
Ch.Wash_Hands.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Wash_Hands")

## test data
test.dat <- subset(movelet.dat, ActivityName %in% c("Turn_Key","Open_Door","6._Med_Taking","7._Med_Taking") & Wrist_Location =="right     ")
test.dat.patient.52 <- Acceleration_Create(test.dat,subjectName="patient52",frequency=300) #3 variables * 100 hz

time.test<- as.numeric(row.names(test.dat))
  
#pred <- Movelet_Pred(test.dat.patient.52, Act.Names=c("Open_water_bottle","Pick_up_and_open_a_pill_bottle","Pour_pill","Take_pill","Eat_From_Bag"), vote=TRUE)

train.label=c( "Open_water_bottle","Pick_up_and_open_a_pill_bottle","Pour_pill","Take_pill","Eat_From_Bag","Pour_Water_into_a_Cup",'Walk','Wash_Hands','Look_around_in_bag_or_purse')

#expand the prediction activity labels to include all trained chapters
#pred <- Movelet_Pred(test.dat.patient.52, Act.Names=train.label, vote=TRUE)
# Save it
#saveRDS(pred, file = "patient52_3rotations_pred.rds")
# load it
patient52_3rotations_pred <- readRDS(file = "patient52_3rotations_pred.rds")
#names(patient52_3rotations_pred$Pred)


##plot the trained vs. observed labels
# dygraph(data=c(dat[time.test,c('time',names(dat)[c(11:13,30)])],pred$Pred),main=paste('Patient', dat$PatientID[1],' Rotation Right Wrist',sep=''))%>% 
#   dyAxis("x", drawGrid = FALSE) %>%
#   dyOptions(colors = RColorBrewer::brewer.pal(7, "Set1"))  %>%
#   dyRangeSelector()


table(patient52_3rotations_pred$Pred)
#dim(test.dat)

time <- seq(1,length(patient52_3rotations_pred$Pred))
plot(x = patient52_3rotations_pred$Pred , y = time, xlab = "Prediction", ylab = "Time", xaxt = "n", pch = 20)
axis(1, at=seq(1,length(train.label)), labels= FALSE)
text(seq(1,length(train.label)),par("usr")[3] - 100, labels = train.label, srt = 45, xpd = TRUE, cex = 0.5, adj = c(1,0))

text(x = 7, y = 90, "Open_Door", cex = 0.5)
abline(h = max(which(test.dat$ActivityName == "Open_Door")), col="red")
text(x = 7, y = 300, "Turn_Key", cex = 0.5)
abline(h = max(which(test.dat$ActivityName == "Turn_Key")), col="red")
text(x = 7, y = 600, "Pick_up_and_open_a_pill_bottle", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 400), col="red")
text(x = 7, y = 920, "Take_pill", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 500), col="red")
text(x = 7, y = 1080, "Drink_water", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 650), col="red")
text(x = 7, y = 1300, "Pick_up_and_open_a_water_bottle_and_put_it_down", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "7._Med_Taking") + 250), col="red")
text(x = 7, y = 1900, "Pick_up_and_open_a_pill_bottle_and_take_pill", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "7._Med_Taking") + 650), col="red")
text(x = 7, y = 2100, "Drink_water", cex = 0.5)

```

<!-- ### Using 3 attitude variables -->

```{r,eval=FALSE, echo = FALSE}
movelet.dat <- dat[,c("attitude_x_coord","attitude_y_coord","attitude_z_coord","ActivityName","Wrist_Location")]
movelet.dat$ActivityName <- gsub(" ", "_", movelet.dat$ActivityName)

## select right wrist
movelet.dat.right <- subset(movelet.dat, Wrist_Location =="right     ")

## create accel data 
patient.52 <- Acceleration_Create(movelet.dat.right,subjectName="patient52",frequency=300) #3 variables * 100 hz
#print.AcceleData(patient.52)

## Train Open_Water_Bottle_and_Take_a_Drink chapter
from <- min(which(patient.52$Label == "Open_Water_Bottle_and_Take_a_Drink"))
to <- max(which(patient.52$Label == "Open_Water_Bottle_and_Take_a_Drink"))
Ch.Open_Water_Bottle_and_Take_a_Drink.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                                                  DATA = patient.52, 
                                                      ChapName = "Open_Water_Bottle_and_Take_a_Drink")
## Train walk chapter
from <- min(which(patient.52$Label == "Walk"))
to <- max(which(patient.52$Label == "Walk"))
Ch.Walk.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Walk")
## Train Pour_Water_into_a_Cup chapter
from <- min(which(patient.52$Label == "Pour_Water_into_a_Cup"))
to <- max(which(patient.52$Label == "Pour_Water_into_a_Cup"))
Ch.Pour_Water_into_a_Cup.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Pour_Water_into_a_Cup")
## train Look_around_in_bag_or_purse chapter
from <- min(which(patient.52$Label == "Look_around_in_bag_or_purse"))
to <- max(which(patient.52$Label == "Look_around_in_bag_or_purse"))
Ch.Look_around_in_bag_or_purse.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Look_around_in_bag_or_purse")
## train eat from bag chapter
from <- min(which(patient.52$Label == "Eat_From_Bag"))
to <- max(which(patient.52$Label == "Eat_From_Bag"))
Ch.Eat_From_Bag.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Eat_From_Bag")

## train open water bottle chapter
from <- min(which(patient.52$Label == "9._Med_Taking")) + 100 ## 12:11:39 picks up water bottle to uncap
to <- max(which(patient.52$Label == "9._Med_Taking")) + 300 ## 12:11:41 returns opened water bottle to table
Ch.Open_water_bottle.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Open_water_bottle")

## train pick up and open a pill bottle chapter
from <- min(which(patient.52$Label == "9._Med_Taking")) + 400 ## 12:11:42 picks up pill bottle
to <- max(which(patient.52$Label == "9._Med_Taking")) + 800 ## 112:11:46 pours pill out into left hand
Ch.Pick_up_and_open_a_pill_bottle.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Pick_up_and_open_a_pill_bottle")
## train pour pill chapter
from <- min(which(patient.52$Label == "9._Med_Taking")) + 800 ## 12:11:46
to <- max(which(patient.52$Label == "9._Med_Taking")) + 900 ## 12:11:47
Ch.Pour_pill.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Pour_pill")

## train take pill chapter 
from <- min(which(patient.52$Label == "9._Med_Taking")) + 900 ## 12:11:47 
to <- max(which(patient.52$Label == "9._Med_Taking")) + 1000 ## 112:11:48
Ch.Take_pill.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Take_pill")

## train Wash_Hands chapter
from <- min(which(patient.52$Label == "Wash_Hands"))
to <- max(which(patient.52$Label == "Wash_Hands"))
Ch.Wash_Hands.patient52 <- Movelet_Create(FROM = from ,TO = to, 
                                    DATA = patient.52, 
                                    ChapName = "Wash_Hands")

## test data
test.dat <- subset(movelet.dat, ActivityName %in% c("Turn_Key","Open_Door","6._Med_Taking","7._Med_Taking") & Wrist_Location =="right     ")
test.dat.patient.52 <- Acceleration_Create(test.dat,subjectName="patient52",frequency=300) #3 variables * 100 hz

time.test<- as.numeric(row.names(test.dat))
  
#pred <- Movelet_Pred(test.dat.patient.52, Act.Names=c("Open_water_bottle","Pick_up_and_open_a_pill_bottle","Pour_pill","Take_pill","Eat_From_Bag"), vote=TRUE)

train.label=c( "Open_water_bottle","Pick_up_and_open_a_pill_bottle","Pour_pill","Take_pill","Eat_From_Bag","Pour_Water_into_a_Cup",'Walk','Wash_Hands','Look_around_in_bag_or_purse')

#expand the prediction activity labels to include all trained chapters
#pred <- Movelet_Pred(test.dat.patient.52, Act.Names=train.label, vote=TRUE)
# Save it
#saveRDS(pred, file = "patient52_3attitudes_pred.rds")
# load it
patient52_3attitudes_pred <- readRDS(file = "patient52_3attitudes_pred.rds")
#names(patient52_3rotations_pred$Pred)


##plot the trained vs. observed labels
# dygraph(data=c(dat[time.test,c('time',names(dat)[c(11:13,30)])],pred$Pred),main=paste('Patient', dat$PatientID[1],' Rotation Right Wrist',sep=''))%>% 
#   dyAxis("x", drawGrid = FALSE) %>%
#   dyOptions(colors = RColorBrewer::brewer.pal(7, "Set1"))  %>%
#   dyRangeSelector()


table(patient52_3attitudes_pred$Pred)
#dim(test.dat)

time <- seq(1,length(patient52_3attitudes_pred$Pred))
plot(x = patient52_3attitudes_pred$Pred , y = time, xlab = "Prediction", ylab = "Time", xaxt = "n", pch = 20)
axis(1, at=seq(1,length(train.label)), labels= FALSE)
text(seq(1,length(train.label)),par("usr")[3] - 100, labels = train.label, srt = 45, xpd = TRUE, cex = 0.5, adj = c(1,0))
text(x = 6, y = 90, "Open_Door", cex = 0.5)
abline(h = max(which(test.dat$ActivityName == "Open_Door")), col="red")
text(x = 6, y = 300, "Turn_Key", cex = 0.5)
abline(h = max(which(test.dat$ActivityName == "Turn_Key")), col="red")
text(x = 6, y = 600, "Pick_up_and_open_a_pill_bottle", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 400), col="red")
text(x = 6, y = 920, "Take_pill", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 500), col="red")
text(x = 6, y = 1080, "Drink_water", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 650), col="red")
text(x = 6, y = 1300, "Pick_up_and_open_a_water_bottle_and_put_it_down", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "7._Med_Taking") + 250), col="red")
text(x = 6, y = 1900, "Pick_up_and_open_a_pill_bottle_and_take_pill", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "7._Med_Taking") + 650), col="red")
text(x = 6, y = 2100, "Drink_water", cex = 0.5)

```

<!-- ### Using 6 variables (3 accels, 3 rotations) -->

```{r, echo = FALSE}
####### Modify movelet_dist to use more variables
## modify movelet packages to have more axes
Acceleration_Create2=function(Data,subjectName,frequency,n_axes,label=TRUE)
{
  if (label==FALSE)
  {Result=list(Subject=subjectName,N=nrow(Data),SampleRate=frequency,Data=Data[,c(1:n_axes)])}
  else {Result=list(Subject=subjectName,N=nrow(Data),SampleRate=frequency,Data=Data[,c(1:n_axes)],Label=Data[,n_axes+1])}
  class(Result)="AcceleData"
  return(Result)
}

Movelet_Create2=function(FROM, TO, DATA, ChapName, n_axes, Length=NULL)
{
  if (is.null(Length)==TRUE)
  {
    Length=DATA$SampleRate
  }
  # define dimension of the movelet collection (number of movelets per collection)
  Dim.Collection = TO-Length+1-FROM+1
  
  # make sure there the time between first and last is greater than Length
  if(Dim.Collection < 1){stop("Movelet length longer than time used")}
  
  # construct dictionary
  # Collection=list(AX1=array(0,c(Dim.Collection,Length)),
  #                 AX2=array(0,c(Dim.Collection,Length)),
  #                 AX3=array(0,c(Dim.Collection,Length)))
  #n_axes <- 6
  Collection <- list()
  for(i in 1:n_axes){
    name <- paste('AX',i,sep='')
    tmp <- array(0,c(Dim.Collection,Length))
    Collection[[name]] <- tmp
  }
  
  temp=c(1:(TO-FROM+1))
  IndexMatrix=c()
  for (t in (0:(Length-1)))
  {
    IndexMatrix=c(IndexMatrix,temp[(1+t):(length(temp)-(Length-t)+1)])
  }
  for (j in 1:n_axes)
  {
    Collection[[j]]=matrix(DATA$Data[IndexMatrix+FROM-1,j],ncol=Length)
  }
  Result=list(Subject=DATA$Subject,Chapter=ChapName,Length=Length,SampleRate=DATA$SampleRate,MvltNum=Dim.Collection,From=FROM, To=TO, Movelet=Collection,Data=DATA$Data[ifelse(FROM-50>0,FROM-50,FROM):ifelse(TO+50<nrow(DATA$Data),TO+50,TO),])
  class(Result)="MvltChap"
  return(Result)
}  
## modify movelet_dist
Movelet_Dist2=function(Chapter, Unlabeled, index=FALSE)
{
  # Check if the class of "Chapter" is MvltChap
  if(class(Chapter)!="MvltChap"){stop("Please use appropriate object for Chapter")}
  # Check if the class of "Unlabeled" is AcceleData
  if(class(Unlabeled)!="AcceleData"){stop("Please use appropriate object for Unlabeled")}  
  N = Unlabeled$N				# length of unlabeled timeseries
  Length = Chapter$Length 	# length of movelets in chapter
  N_Chapter=Chapter$MvltNum	# number of chapter elements
  
  # decompose unlabeled timeseries into movelets
  Unlabeled_Movelets=Movelet_Create2(FROM=1, TO=N, DATA=Unlabeled, 
                                     Length=Length, n_axes = 6, ChapName="Unlabeled")
  
  N_Sample=Unlabeled_Movelets$MvltNum	# number of unlabeled movelets
  Distance=array(0,c(N_Sample,N_Chapter))
  for (i in 1:N_Chapter)
  {
    Dist1=sqrt(apply((t(t(Unlabeled_Movelets$Movelet$AX1)-Chapter$Movelet$AX1[i,]))^2,1,sum))
    Dist2=sqrt(apply((t(t(Unlabeled_Movelets$Movelet$AX2)-Chapter$Movelet$AX2[i,]))^2,1,sum))
    Dist3=sqrt(apply((t(t(Unlabeled_Movelets$Movelet$AX3)-Chapter$Movelet$AX3[i,]))^2,1,sum))
    Dist4=sqrt(apply((t(t(Unlabeled_Movelets$Movelet$AX4)-Chapter$Movelet$AX4[i,]))^2,1,sum))
    Dist5=sqrt(apply((t(t(Unlabeled_Movelets$Movelet$AX5)-Chapter$Movelet$AX5[i,]))^2,1,sum))
    Dist6=sqrt(apply((t(t(Unlabeled_Movelets$Movelet$AX6)-Chapter$Movelet$AX6[i,]))^2,1,sum))
    Dist=(Dist1+Dist2+Dist3+Dist4+Dist5+Dist6)/6
    Distance[,i]=Dist
  }
  Result=array(0,c(2,N_Sample))
  Result[1,]=apply(Distance,1,which.min)
  Result[2,]=apply(Distance,1,min)
  if (index==FALSE)
  {
    return(Result[2,])
  } else 
  {
    return(Result)
  }
}

Movelet_Pred2=function(x,Act.Names,vote=FALSE)
{
  Ch.Names = paste("Ch.", Act.Names, ".",x$Subject,sep="")
  Distance = c()
  Length=get(Ch.Names[1])$Length
  for(i in 1:length(Act.Names))
  {
    Distance = cbind(Distance, Movelet_Dist2(get(Ch.Names[i]),x))
  }
  
  Distance=as.data.frame(Distance)
  colnames(Distance) = Act.Names
  
  ## estimate predicited activity as using the minimum distance
  Predicted.Labels=sapply(1:dim(Distance)[1], function(u) which.min(Distance[u,]))
  Result=Predicted.Labels
  ## Voting ##
  if (vote==TRUE)
  {
    for (i in 1:length(Predicted.Labels))
    {
      Start=max(1,i-Length+1)
      End=min(length(Predicted.Labels),i)
      Table=table(Predicted.Labels[Start:End])
      #       W=1
      #       Table[which(as.character(Predicted.Labels[Start+3])==names(table(Predicted.Labels[Start:End])))]=Table[which(as.character(Predicted.Labels[Start+3])==names(table(Predicted.Labels[Start:End])))]+W
      #       Table[which(as.character(Predicted.Labels[Start+4])==names(table(Predicted.Labels[Start:End])))]=Table[which(as.character(Predicted.Labels[Start+4])==names(table(Predicted.Labels[Start:End])))]+W
      #       Table[which(as.character(Predicted.Labels[Start+5])==names(table(Predicted.Labels[Start:End])))]=Table[which(as.character(Predicted.Labels[Start+5])==names(table(Predicted.Labels[Start:End])))]+W
      #       Table[which(as.character(Predicted.Labels[Start+6])==names(table(Predicted.Labels[Start:End])))]=Table[which(as.character(Predicted.Labels[Start+6])==names(table(Predicted.Labels[Start:End])))]+W
      Result[i]=as.numeric(names(which.max(Table)))
    }
  }
  return(list(Dist=Distance, Pred=Result))  
}
```


```{r, eval = FALSE, echo = FALSE}
movelet.dat <- dat[,c("accel_x_coord","accel_y_coord","accel_z_coord",
                      "rotate_x_coord","rotate_y_coord","rotate_z_coord",
                      "ActivityName","Wrist_Location")]
movelet.dat$ActivityName <- gsub(" ", "_", movelet.dat$ActivityName)
## select right wrist
movelet.dat.right <- subset(movelet.dat, Wrist_Location =="right     ")
## create accel data 
patient.52 <- Acceleration_Create2(movelet.dat.right,subjectName="patient52",
                                   n_axes = 6,frequency=100) # 6 variables * 100 hz = 600?? 
## Train Open_Water_Bottle_and_Take_a_Drink chapter
from <- min(which(patient.52$Label == "Open_Water_Bottle_and_Take_a_Drink"))
to <- max(which(patient.52$Label == "Open_Water_Bottle_and_Take_a_Drink"))
Ch.Open_Water_Bottle_and_Take_a_Drink.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
                                                                  DATA = patient.52, n_axes = 6,
                                                      ChapName = "Open_Water_Bottle_and_Take_a_Drink")
## Train walk chapter
from <- min(which(patient.52$Label == "Walk"))
to <- max(which(patient.52$Label == "Walk"))
Ch.Walk.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
                                    DATA = patient.52, n_axes = 6,
                                    ChapName = "Walk")
## Train Pour_Water_into_a_Cup chapter
from <- min(which(patient.52$Label == "Pour_Water_into_a_Cup"))
to <- max(which(patient.52$Label == "Pour_Water_into_a_Cup"))
Ch.Pour_Water_into_a_Cup.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
                                    DATA = patient.52, n_axes = 6,
                                    ChapName = "Pour_Water_into_a_Cup")
## train Look_around_in_bag_or_purse chapter
from <- min(which(patient.52$Label == "Look_around_in_bag_or_purse"))
to <- max(which(patient.52$Label == "Look_around_in_bag_or_purse"))
Ch.Look_around_in_bag_or_purse.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
                                    DATA = patient.52, n_axes = 6, 
                                    ChapName = "Look_around_in_bag_or_purse")
## train eat from bag chapter
from <- min(which(patient.52$Label == "Eat_From_Bag"))
to <- max(which(patient.52$Label == "Eat_From_Bag"))
Ch.Eat_From_Bag.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
                                    DATA = patient.52, n_axes = 6,
                                    ChapName = "Eat_From_Bag")

## train open water bottle chapter
from <- min(which(patient.52$Label == "9._Med_Taking")) + 100 ## 12:11:39 picks up water bottle to uncap
to <- max(which(patient.52$Label == "9._Med_Taking")) + 300 ## 12:11:41 returns opened water bottle to table
Ch.Open_water_bottle.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
                                    DATA = patient.52, n_axes = 6,
                                    ChapName = "Open_water_bottle")

## train pick up and open a pill bottle chapter
from <- min(which(patient.52$Label == "9._Med_Taking")) + 400 ## 12:11:42 picks up pill bottle
to <- max(which(patient.52$Label == "9._Med_Taking")) + 800 ## 112:11:46 pours pill out into left hand
Ch.Pick_up_and_open_a_pill_bottle.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
                                    DATA = patient.52, n_axes = 6,
                                    ChapName = "Pick_up_and_open_a_pill_bottle")
## train pour pill chapter
from <- min(which(patient.52$Label == "9._Med_Taking")) + 800 ## 12:11:46
to <- max(which(patient.52$Label == "9._Med_Taking")) + 900 ## 12:11:47
Ch.Pour_pill.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
                                    DATA = patient.52, n_axes = 6,
                                    ChapName = "Pour_pill")

## train take pill chapter 
from <- min(which(patient.52$Label == "9._Med_Taking")) + 900 ## 12:11:47 
to <- max(which(patient.52$Label == "9._Med_Taking")) + 1000 ## 112:11:48
Ch.Take_pill.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
                                    DATA = patient.52, n_axes = 6,
                                    ChapName = "Take_pill")

## train Wash_Hands chapter
from <- min(which(patient.52$Label == "Wash_Hands"))
to <- max(which(patient.52$Label == "Wash_Hands"))
Ch.Wash_Hands.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
                                    DATA = patient.52, n_axes = 6,
                                    ChapName = "Wash_Hands")

## test data
test.dat <- subset(movelet.dat, ActivityName %in% c("Turn_Key","Open_Door","6._Med_Taking","7._Med_Taking") & Wrist_Location =="right     ")
test.dat.patient.52 <- Acceleration_Create2(test.dat,subjectName="patient52",n_axes = 6,frequency=100) #6 variables * 100 hz

time.test<- as.numeric(row.names(test.dat))
  
#pred <- Movelet_Pred(test.dat.patient.52, Act.Names=c("Open_water_bottle","Pick_up_and_open_a_pill_bottle","Pour_pill","Take_pill","Eat_From_Bag"), vote=TRUE)

train.label=c( "Open_water_bottle","Pick_up_and_open_a_pill_bottle","Pour_pill","Take_pill","Eat_From_Bag","Pour_Water_into_a_Cup",'Walk','Wash_Hands','Look_around_in_bag_or_purse')

#expand the prediction activity labels to include all trained chapters
#pred <- Movelet_Pred2(test.dat.patient.52, Act.Names=train.label, vote=TRUE)
# Save it
#saveRDS(pred, file = "patient52_6vars_pred.rds")
# load it
patient52_6vars_pred <- readRDS(file = "patient52_6vars_pred.rds")
#names(patient52_3accels_pred$Pred)
##plot the trained vs. observed labels
# dygraph(data=c(dat[time.test,c('time',names(dat)[c(11:13,30)])],pred$Pred),main=paste('Patient', dat$PatientID[1],' Rotation Right Wrist',sep=''))%>% 
#   dyAxis("x", drawGrid = FALSE) %>%
#   dyOptions(colors = RColorBrewer::brewer.pal(7, "Set1"))  %>%
#   dyRangeSelector()


table(patient52_6vars_pred$Pred)
#dim(test.dat)

time <- seq(1,length(patient52_6vars_pred$Pred))
plot(x = patient52_6vars_pred$Pred , y = time, xlab = "Prediction", ylab = "Time", xaxt = "n", pch = 20)
axis(1, at=seq(1,length(train.label)), labels= FALSE)
text(seq(1,length(train.label)),par("usr")[3] - 100, labels = train.label, srt = 45, xpd = TRUE, cex = 0.5, adj = c(1,0))
text(x = 1.5, y = 90, "Open_Door", cex = 0.5)
abline(h = max(which(test.dat$ActivityName == "Open_Door")), col="red")
text(x = 1.5, y = 300, "Turn_Key", cex = 0.5)
abline(h = max(which(test.dat$ActivityName == "Turn_Key")), col="red")
text(x = 1.5, y = 600, "Pick_up_and_open_a_pill_bottle", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 400), col="red")
text(x = 1.5, y = 920, "Take_pill", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 500), col="red")
text(x = 1.5, y = 1080, "Drink_water", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 650), col="red")
text(x = 1.5, y = 1300, "Pick_up_and_open_a_water_bottle_and_put_it_down", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "7._Med_Taking") + 250), col="red")
text(x = 1.5, y = 1900, "Pick_up_and_open_a_pill_bottle_and_take_pill", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "7._Med_Taking") + 650), col="red")
text(x = 1.5, y = 2100, "Drink_water", cex = 0.5)
```



<!-- ### Using 6 PCs for all 15 variables of right hands -->

```{r,eval=FALSE, echo = FALSE}
#names(dat)
#### perform PCA on 15 variables of the right hand
## recode the wrist location variable
dat$Wrist_Location <- ifelse(dat$Wrist_Location =="right     ","right","left")
table(dat$Wrist_Location)

varss <- dat[dat$Wrist_Location =="right",c("accel_x_coord","accel_y_coord","accel_z_coord",
                "rotate_x_coord","rotate_y_coord", "rotate_z_coord",
                "gravity_x_coord","gravity_z_coord","gravity_y_coord",
                "magneto_x_coord","magneto_y_coord","magneto_z_coord",
                "attitude_x_coord","attitude_y_coord","attitude_z_coord")]
varss.pca <- prcomp(varss, center=TRUE, scale.=TRUE)
summary(varss.pca)
pcs <- varss.pca$x[,1:6] ## the 6 PCs for movelet

## check pc plots
#fviz_pca_var(varss.pca,axes = c(1, 2))
#fviz_pca_var(varss.pca,axes = c(3, 4))
#fviz_pca_var(varss.pca,axes = c(5, 6))
varss.pca$rotation[,1:6]
```

<!-- PC1 is mainly contributed by the 3 magneto measurements. Similarly, for PC2 we have gravity_y, gravity_z and attitude_y (some combination of the y-axes); PC3 we have gravity_x and attitude_x (some combination of the x-axes); PC4 we have accel_y, rotate_x, rotate_y; PC5 we have accel_z, rotate_y; PC6 we have accel_x, accel_y and some rotate_z.  -->

```{r,eval=FALSE,, echo = FALSE}
movelet.dat <- cbind(pcs, dat[dat$Wrist_Location == "right",c("ActivityName","Wrist_Location")])
movelet.dat$ActivityName <- gsub(" ", "_", movelet.dat$ActivityName)

## create accel data 
patient.52 <- Acceleration_Create2(movelet.dat,subjectName="patient52",
                                   n_axes = 6,frequency=100) # 6 variables * 100 hz = 600?? 
# ## Train Open_Water_Bottle_and_Take_a_Drink chapter
# from <- min(which(patient.52$Label == "Open_Water_Bottle_and_Take_a_Drink"))
# to <- max(which(patient.52$Label == "Open_Water_Bottle_and_Take_a_Drink"))
# Ch.Open_Water_Bottle_and_Take_a_Drink.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
#                                                                   DATA = patient.52, n_axes = 6,
#                                                       ChapName = "Open_Water_Bottle_and_Take_a_Drink")
# ## Train walk chapter
# from <- min(which(patient.52$Label == "Walk"))
# to <- max(which(patient.52$Label == "Walk"))
# Ch.Walk.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
#                                     DATA = patient.52, n_axes = 6,
#                                     ChapName = "Walk")
# ## Train Pour_Water_into_a_Cup chapter
# from <- min(which(patient.52$Label == "Pour_Water_into_a_Cup"))
# to <- max(which(patient.52$Label == "Pour_Water_into_a_Cup"))
# Ch.Pour_Water_into_a_Cup.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
#                                     DATA = patient.52, n_axes = 6,
#                                     ChapName = "Pour_Water_into_a_Cup")
# ## train Look_around_in_bag_or_purse chapter
# from <- min(which(patient.52$Label == "Look_around_in_bag_or_purse"))
# to <- max(which(patient.52$Label == "Look_around_in_bag_or_purse"))
# Ch.Look_around_in_bag_or_purse.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
#                                     DATA = patient.52, n_axes = 6, 
#                                     ChapName = "Look_around_in_bag_or_purse")
## train eat from bag chapter
# from <- min(which(patient.52$Label == "Eat_From_Bag"))
# to <- max(which(patient.52$Label == "Eat_From_Bag"))
# Ch.Eat_From_Bag.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
#                                     DATA = patient.52, n_axes = 6,
#                                     ChapName = "Eat_From_Bag")

# ## train open water bottle chapter
# from <- min(which(patient.52$Label == "9._Med_Taking")) + 100 ## 12:11:39 picks up water bottle to uncap
# to <- max(which(patient.52$Label == "9._Med_Taking")) + 300 ## 12:11:41 returns opened water bottle to table
# Ch.Pick_up_bottle.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
#                                     DATA = patient.52, n_axes = 6,
#                                     ChapName = "Pick_up_bottle")

## train pick up and open a pill bottle chapter
from <- min(which(patient.52$Label == "9._Med_Taking")) + 200 ## 12:11:42 picks up pill bottle
to <- min(which(patient.52$Label == "9._Med_Taking")) + 400 ## 112:11:46
Ch.Pick_up_and_open_pill_bottle.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
                                    DATA = patient.52, n_axes = 6,
                                    ChapName = "Pick_up_and_open_pill_bottle")
# ## train pour pill chapter
# from <- min(which(patient.52$Label == "9._Med_Taking")) + 400 ## 12:11:46
# to <- min(which(patient.52$Label == "9._Med_Taking")) + 450 ## 12:11:47
# Ch.Pour_pill.patient52 <- Movelet_Create2(FROM = from ,TO = to,
#                                     DATA = patient.52, n_axes = 6,
#                                     ChapName = "Pour_pill")

## train pour and take pill chapter 
from <- min(which(patient.52$Label == "9._Med_Taking")) + 400 ## 12:11:46 
to <- min(which(patient.52$Label == "9._Med_Taking")) + 500 ## 112:11:48
Ch.Pour_and_take_pill.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
                                    DATA = patient.52, n_axes = 6,
                                    ChapName = "Pour_and_take_pill")

## train Wash_Hands chapter
from <- min(which(patient.52$Label == "Wash_Hands"))
to <- max(which(patient.52$Label == "Wash_Hands"))
Ch.Wash_Hands.patient52 <- Movelet_Create2(FROM = from ,TO = to,
                                    DATA = patient.52, n_axes = 6,
                                    ChapName = "Wash_Hands")

## test data
test.dat <- subset(movelet.dat, ActivityName %in% c("Turn_Key","Open_Door","6._Med_Taking","7._Med_Taking"))
test.dat.patient.52 <- Acceleration_Create2(test.dat,subjectName="patient52",n_axes = 6,frequency=100) #6 variables * 100 hz
train.label=c("Pick_up_and_open_pill_bottle","Pour_and_take_pill","Wash_Hands")
```

```{r, eval=FALSE, echo = FALSE}
#expand the prediction activity labels to include all trained chapters
pred <- Movelet_Pred2(test.dat.patient.52, Act.Names=train.label, vote=TRUE)
# Save it
saveRDS(pred, file = "patient52_6pcs_right_pred.rds")
```

```{r,eval=FALSE, echo = FALSE}
# load it
patient52_6pcs_right_pred <- readRDS(file = "patient52_6pcs_right_pred.rds")

##plot the trained vs. observed labels
# dygraph(data=c(dat[time.test,c('time',names(dat)[c(11:13,30)])],pred$Pred),main=paste('Patient', dat$PatientID[1],' Rotation Right Wrist',sep=''))%>% 
#   dyAxis("x", drawGrid = FALSE) %>%
#   dyOptions(colors = RColorBrewer::brewer.pal(7, "Set1"))  %>%
#   dyRangeSelector()
#table(patient52_6pcs_right_pred$Pred)


time <- seq(1,length(patient52_6pcs_right_pred$Pred))
plot(x = patient52_6pcs_right_pred$Pred , y = time, xlab = "Prediction", ylab = "Time", xaxt = "n", pch = 20)
axis(1, at=seq(1,length(train.label)), labels= FALSE)
text(seq(1,length(train.label)),par("usr")[3] - 100, labels = train.label, srt = 45, xpd = TRUE, cex = 0.5, adj = c(1,0))
text(x = 2.5, y = 90, "Open_Door", cex = 0.5)
abline(h = max(which(test.dat$ActivityName == "Open_Door")), col="red")
text(x = 2.5, y = 300, "Turn_Key", cex = 0.5)
abline(h = max(which(test.dat$ActivityName == "Turn_Key")), col="red")
text(x = 2.5, y = 600, "Pick_up_and_open_a_pill_bottle", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 250), col="red")
text(x = 2.5, y = 800, "Pour_pill", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 400), col="red")
text(x = 2.5, y = 1000, "Take_pill_and_the_rest", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "7._Med_Taking")), col="red")
text(x = 2.5, y = 1500, "Pick_up_and_open_a_water_bottle_and_pill_bottle", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "7._Med_Taking") + 450), col="red")
text(x = 2.5, y = 1900, "Pour_pill", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "7._Med_Taking") + 600), col="red")
text(x = 2.5, y = 2200, "Take_pill", cex = 0.5)
```





<!-- ### Using 6 PCs for all 15 variables of the left hand -->
```{r}
# table(dat$Wrist_Location)
# x = dat$Wrist_Location == "left      "
# test <- ave(x, cumsum(!x), FUN = cumsum)
# table(test)
# which(test > 1)
# x.rm.left <- dat$Wrist_Location[-which(test > 1)]
# table(x.rm.left)


```

```{r,eval=FALSE, echo = FALSE}
#names(dat)
#### perform PCA on 15 variables of the right hand

varss <- dat[dat$Wrist_Location =="left",c("accel_x_coord","accel_y_coord","accel_z_coord",
                "rotate_x_coord","rotate_y_coord", "rotate_z_coord",
                "gravity_x_coord","gravity_z_coord","gravity_y_coord",
                "magneto_x_coord","magneto_y_coord","magneto_z_coord",
                "attitude_x_coord","attitude_y_coord","attitude_z_coord")]
varss.pca <- prcomp(varss, center=TRUE, scale.=TRUE)
summary(varss.pca)
pcs <- varss.pca$x[,1:6] ## the 6 PCs for movelet

## check pc plots
#fviz_pca_var(varss.pca,axes = c(1, 2))
#fviz_pca_var(varss.pca,axes = c(3, 4))
#fviz_pca_var(varss.pca,axes = c(5, 6))
varss.pca$rotation[,1:6]
```

<!-- PC1 is mainly contributed by the gravity_x, magneto_x and attitude_x. Similarly, for PC2 we have gravity_y, magneto_y and attitude_y (some combination of the y-axes); PC3 we have gravity_z and magneto_z (some combination of the z-axes); PC4 we have rotate_x, rotate_y and rotate_z; PC5 we have accel_x, accel_z, rotate_z; PC6 we have accel_y, accel_z. -->

```{r,eval=FALSE, echo = FALSE}
movelet.dat <- cbind(pcs, dat[dat$Wrist_Location == "left",c("ActivityName","Wrist_Location")])
movelet.dat$ActivityName <- gsub(" ", "_", movelet.dat$ActivityName)

## create accel data 
patient.52 <- Acceleration_Create2(movelet.dat,subjectName="patient52",
                                   n_axes = 6,frequency=100) # 6 variables * 100 hz = 600?? 
## train pick up and open a pill bottle chapter
from <- min(which(patient.52$Label == "9._Med_Taking")) + 200 ## 12:11:42 picks up pill bottle
to <- min(which(patient.52$Label == "9._Med_Taking")) + 400 ## 112:11:46
Ch.Pick_up_and_open_pill_bottle.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
                                    DATA = patient.52, n_axes = 6,
                                    ChapName = "Pick_up_and_open_pill_bottle")
# ## train pour pill chapter
# from <- min(which(patient.52$Label == "9._Med_Taking")) + 400 ## 12:11:46
# to <- min(which(patient.52$Label == "9._Med_Taking")) + 450 ## 12:11:47
# Ch.Pour_pill.patient52 <- Movelet_Create2(FROM = from ,TO = to,
#                                     DATA = patient.52, n_axes = 6,
#                                     ChapName = "Pour_pill")

## train pour and take pill chapter 
from <- min(which(patient.52$Label == "9._Med_Taking")) + 400 ## 12:11:46 
to <- min(which(patient.52$Label == "9._Med_Taking")) + 500 ## 112:11:48
Ch.Pour_and_take_pill.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
                                    DATA = patient.52, n_axes = 6,
                                    ChapName = "Pour_and_take_pill")

## train Wash_Hands chapter
from <- min(which(patient.52$Label == "Wash_Hands"))
to <- max(which(patient.52$Label == "Wash_Hands"))
Ch.Wash_Hands.patient52 <- Movelet_Create2(FROM = from ,TO = to,
                                    DATA = patient.52, n_axes = 6,
                                    ChapName = "Wash_Hands")
## test data
test.dat <- subset(movelet.dat, ActivityName %in% c("Turn_Key","Open_Door","6._Med_Taking","7._Med_Taking"))
test.dat.patient.52 <- Acceleration_Create2(test.dat,subjectName="patient52",n_axes = 6,frequency=100) #6 variables * 100 hz
train.label=c("Pick_up_and_open_pill_bottle","Pour_and_take_pill","Wash_Hands")
```

```{r, eval = FALSE, echo = FALSE}
#expand the prediction activity labels to include all trained chapters
pred <- Movelet_Pred2(test.dat.patient.52, Act.Names=train.label, vote=TRUE)
# Save it
saveRDS(pred, file = "patient52_6pcs_left_pred.rds")
```

```{r,eval=FALSE, echo = FALSE}
# load it
patient52_6pcs_left_pred <- readRDS(file = "patient52_6pcs_left_pred.rds")
table(patient52_6pcs_left_pred$Pred)
## plot results
time <- seq(1,length(patient52_6pcs_left_pred$Pred))
plot(x = patient52_6pcs_left_pred$Pred , y = time, xlab = "Prediction", ylab = "Time", xaxt = "n", pch = 20)
axis(1, at=seq(1,length(train.label)), labels= FALSE)
text(seq(1,length(train.label)),par("usr")[3] - 100, labels = train.label, srt = 45, xpd = TRUE, cex = 0.5, adj = c(1,0))
text(x = 1.5, y = 90, "Open_Door", cex = 0.5)
abline(h = max(which(test.dat$ActivityName == "Open_Door")), col="red")
text(x = 1.5, y = 300, "Turn_Key", cex = 0.5)
abline(h = max(which(test.dat$ActivityName == "Turn_Key")), col="red")
text(x = 1.5, y = 600, "Pick_up_and_open_a_pill_bottle", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 250), col="red")
text(x = 1.5, y = 800, "Pour_pill", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 400), col="red")
text(x = 1.5, y = 1000, "Take_pill_and_the_rest", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "7._Med_Taking")), col="red")
text(x = 1.5, y = 1500, "Pick_up_and_open_a_water_bottle_and_pill_bottle", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "7._Med_Taking") + 450), col="red")
text(x = 1.5, y = 1900, "Pour_pill", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "7._Med_Taking") + 600), col="red")
text(x = 1.5, y = 2200, "Take_pill", cex = 0.5)
```

### Using 6 PCs for all 15 variables of both hands

```{r, eval = FALSE, echo = FALSE}
#names(dat)
#### perform PCA on 15 variables of both hands
varss <- dat[ ,c("accel_x_coord","accel_y_coord","accel_z_coord",
                "rotate_x_coord","rotate_y_coord", "rotate_z_coord",
                "gravity_x_coord","gravity_z_coord","gravity_y_coord",
                "magneto_x_coord","magneto_y_coord","magneto_z_coord",
                "attitude_x_coord","attitude_y_coord","attitude_z_coord")]
varss.pca <- prcomp(varss, center=TRUE, scale.=TRUE)
summary(varss.pca)
pcs <- varss.pca$x[,1:6] ## the 6 PCs for movelet

## check pc plots
#fviz_pca_var(varss.pca,axes = c(1, 2))
#fviz_pca_var(varss.pca,axes = c(3, 4))
#fviz_pca_var(varss.pca,axes = c(5, 6))
varss.pca$rotation[,1:6]
```

<!-- PC1 is mainly contributed by the 3 magnetos. For PC2 we have gravity_y, attitude_y (some combination of the y-axes); PC3 we have gravity_x and attitude_x and attitude_z (some combination of the x-axes); PC4 we have accel_y and gravity_z; PC5 we have rotation_x, rotation_y, rotation_z; PC6 we have accel_x, accel_z. -->

```{r, echo = FALSE}
## Relabel names for wrist location
dat$Wrist_Location <- ifelse(dat$Wrist_Location =="right     ","right","left")

## remove duplicate left and right wrist to create balance data
dat$Wrist_Location2 <- ifelse(dat$Wrist_Location == "left", 0, 1)
keep_idx <- c()
diff_time <- diff(dat$time)
diff_wrist <- diff(dat$Wrist_Location2)

for (i in 1:length(diff_time)){
  if (diff_time[i] <= 0.01 & diff_wrist[i] != 0)
  {
    keep_idx = c(keep_idx, i, i + 1) 
  }
  i = i + 2
}
nodup_dat <- dat[keep_idx, ]
table(nodup_dat$Wrist_Location)
```

```{r}
## extract 3 pcs for the left hand
vars_left <- nodup_dat[nodup_dat$Wrist_Location=="left",
                       c("accel_x_coord","accel_y_coord","accel_z_coord",
                        "rotate_x_coord","rotate_y_coord", "rotate_z_coord",
                        "gravity_x_coord","gravity_z_coord","gravity_y_coord",
                        "magneto_x_coord","magneto_y_coord","magneto_z_coord",
                        "attitude_x_coord","attitude_y_coord","attitude_z_coord")]
varsleft.pca <- prcomp(vars_left, center=TRUE, scale=TRUE)
#summary(varsleft.pca)
pcs_left <- varsleft.pca$x[,1:3]

## extract 3 pcs for the right hand
vars_right <- nodup_dat[nodup_dat$Wrist_Location=="right",
                       c("accel_x_coord","accel_y_coord","accel_z_coord",
                        "rotate_x_coord","rotate_y_coord", "rotate_z_coord",
                        "gravity_x_coord","gravity_z_coord","gravity_y_coord",
                        "magneto_x_coord","magneto_y_coord","magneto_z_coord",
                        "attitude_x_coord","attitude_y_coord","attitude_z_coord")]
varsright.pca <- prcomp(vars_right, center=TRUE, scale.=TRUE)
#summary(varsright.pca)
pcs_right <- varsright.pca$x[,1:3]

pcs_combined <- cbind(pcs_left,pcs_right)
colnames(pcs_combined) <- c("PC1_left","PC2_left","PC3_left","PC1_right","PC2_right","PC3_right")
```

```{r}
# dat$Time <- c(1:nrow(dat))
# table(dat$Wrist_Location)

## combine data with Pcs
ActivityName <- nodup_dat$ActivityName[nodup_dat$Wrist_Location=="left"]
movelet.dat <- data.frame(pcs_combined, ActivityName)
movelet.dat$ActivityName <- gsub(" ", "_", movelet.dat$ActivityName)

## Reorder movelet into left hand then right hand for each activity
#movelet.dat <- movelet.dat[order(movelet.dat$ActivityName,movelet.dat$Wrist_Location),]

## create accel data 
patient.52 <- Acceleration_Create2(movelet.dat,subjectName="patient52",
                                   n_axes = 6,frequency=50) # 50 obs per second
## train pick up and open a pill bottle chapter
## 9._Med_Taking is about 24 seconds, about 1200 observations, so 1 sec = 50 obs. 
from <- min(which(patient.52$Label == "9._Med_Taking")) + 200 ## 12:11:42 picks up pill bottle
to <- min(which(patient.52$Label == "9._Med_Taking")) + 400 ## 112:11:46
Ch.Pick_up_and_open_pill_bottle.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
                                    DATA = patient.52, n_axes = 6,
                                    ChapName = "Pick_up_and_open_pill_bottle")
# ## train pour pill chapter
# from <- min(which(patient.52$Label == "9._Med_Taking")) + 800 ## 12:11:46
# to <- min(which(patient.52$Label == "9._Med_Taking")) + 900 ## 12:11:47
# Ch.Pour_pill.patient52 <- Movelet_Create2(FROM = from ,TO = to,
#                                     DATA = patient.52, n_axes = 6,
#                                     ChapName = "Pour_pill")

## train take pill chapter 
from <- min(which(patient.52$Label == "9._Med_Taking")) + 400 ## 12:11:46 
to <- min(which(patient.52$Label == "9._Med_Taking")) + 500 ## 112:11:48
Ch.Pour_pill_return_bottle_and_take_pill.patient52 <- Movelet_Create2(FROM = from ,TO = to, 
                                    DATA = patient.52, n_axes = 6,
                                    ChapName = "Pour_pill_return_bottle_and_take_pill")

## train Wash_Hands chapter
from <- min(which(patient.52$Label == "Wash_Hands"))
to <- max(which(patient.52$Label == "Wash_Hands"))
Ch.Wash_Hands.patient52 <- Movelet_Create2(FROM = from ,TO = to,
                                    DATA = patient.52, n_axes = 6,
                                    ChapName = "Wash_Hands")
## train Look_around_in_bag_or_purse chapter
from <- min(which(patient.52$Label == "Look_around_in_bag_or_purse"))
to <- max(which(patient.52$Label == "Look_around_in_bag_or_purse"))
Ch.Look_around_in_bag_or_purse.patient52 <- Movelet_Create2(FROM = from ,TO = to,
                                    DATA = patient.52, n_axes = 6,
                                    ChapName = "Look_around_in_bag_or_purse")
## test data
test.dat <- subset(movelet.dat, ActivityName %in% c("Walk","Turn_Key","Open_Door","Eat_From_Bag","6._Med_Taking","7._Med_Taking","4._Med_Taking","5._Med_Taking","8._Med_Taking","10._Med_Taking","11._Med_Taking","12._Med_Taking"))
test.dat.patient.52 <- Acceleration_Create2(test.dat,subjectName="patient52",n_axes = 6,frequency=50) 
train.label=c("Pick_up_and_open_pill_bottle","Pour_pill_return_bottle_and_take_pill","Wash_Hands","Look_around_in_bag_or_purse")
```

```{r, eval = FALSE}
#expand the prediction activity labels to include all trained chapters
pred <- Movelet_Pred2(test.dat.patient.52, Act.Names=train.label, vote=TRUE)
# Save it
#saveRDS(pred, file = "patient52_6pcs_both_separated_wrists_pred.rds")
saveRDS(pred, file = "patient52_8_meds.rds")
```

```{r}
# load it
patient52_8_meds <- readRDS(file = "patient52_8_meds.rds")
patient52_8_meds$Pred2 <- recode(patient52_8_meds$Pred, `1`="Pick_up_and_open_pill_bottle", `2`="Pour_pill_return_bottle_and_take_pill", `3`="Wash_Hands", `4`="Look_around_in_bag_or_purse")
```

```{r, eval = FALSE, echo = FALSE}
## plot results
time <- seq(1,length(patient52_8_meds$Pred))
plot(x = patient52_8_meds$Pred , y = time, xlab = "Prediction", ylab = "Time", xaxt = "n", pch = 20, cex = 0.1)
axis(1, at=seq(1,length(train.label)), labels= FALSE)
text(seq(1,length(train.label)),par("usr")[3] - 100, labels = train.label, srt = 30, xpd = TRUE, cex = 0.5, adj = c(1,0))
text(x = 1.5, y = 90, "Open_Door", cex = 0.5)
abline(h = max(which(test.dat$ActivityName == "Open_Door")), col="red")
text(x = 1.5, y = 250, "Turn_Key", cex = 0.5)
abline(h = max(which(test.dat$ActivityName == "Turn_Key")), col="red")
#abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 200), col="red")
text(x = 1.5, y = min(which(test.dat$ActivityName == "6._Med_Taking") + 125), "Pick_up_and_open_a_pill_bottle", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 250), col="red")
#text(x = 1.5, y = min(which(test.dat$ActivityName == "6._Med_Taking") + 650), "Pour_pill", cex = 0.5)
#abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 800), col="red")
text(x = 1.5, y = min(which(test.dat$ActivityName == "6._Med_Taking") + 375), "Pour_pill_return_bottle_and_take_pill", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 500), col="red")
text(x = 1.5, y = min(which(test.dat$ActivityName == "6._Med_Taking") + 600), "Others", cex = 0.5)

abline(h = min(which(test.dat$ActivityName == "7._Med_Taking")), col="red")
text(x = 1.5, y = min(which(test.dat$ActivityName == "7._Med_Taking") + 225), "Pick_up_and_open_a_water_bottle_and_pill_bottle", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "7._Med_Taking") + 450), col="red")
text(x = 1.5, y = min(which(test.dat$ActivityName == "7._Med_Taking") + 550), "Pour_pill_return_bottle_and_take_pill", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "7._Med_Taking") + 650), col="red")
# text(x = 1.5, y = min(which(test.dat$ActivityName == "7._Med_Taking") + 1250), "Take_pill", cex = 0.5)
# abline(h = min(which(test.dat$ActivityName == "7._Med_Taking") + 1300), col="red")
text(x = 1.5, y = min(which(test.dat$ActivityName == "7._Med_Taking") + 800), "Others", cex = 0.5)
```

```{r, eval = FALSE, echo = FALSE}
# load it
patient52_6pcs_both_separated_wrists_pred <- readRDS(file = "patient52_6pcs_both_separated_wrists_pred.rds")
#table(patient52_6pcs_both_separated_wrists_pred$Pred)
patient52_6pcs_both_separated_wrists_pred$Pred2 <- ifelse(patient52_6pcs_both_separated_wrists_pred$Pred == 1, "Pick_up_and_open_pill_bottle", ifelse(patient52_6pcs_both_separated_wrists_pred$Pred == 2, "Pour_pill_return_bottle_and_take_pill","Wash_Hands"))
table(patient52_6pcs_both_separated_wrists_pred$Pred2)

## plot results
time <- seq(1,length(patient52_6pcs_both_separated_wrists_pred$Pred))
plot(x = patient52_6pcs_both_separated_wrists_pred$Pred , y = time, xlab = "Prediction", ylab = "Time", xaxt = "n", pch = 20, cex = 0.1)
axis(1, at=seq(1,length(train.label)), labels= FALSE)
text(seq(1,length(train.label)),par("usr")[3] - 100, labels = train.label, srt = 30, xpd = TRUE, cex = 0.5, adj = c(1,0))
text(x = 1.5, y = 90, "Open_Door", cex = 0.5)
abline(h = max(which(test.dat$ActivityName == "Open_Door")), col="red")
text(x = 1.5, y = 250, "Turn_Key", cex = 0.5)
abline(h = max(which(test.dat$ActivityName == "Turn_Key")), col="red")
#abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 200), col="red")
text(x = 1.5, y = min(which(test.dat$ActivityName == "6._Med_Taking") + 125), "Pick_up_and_open_a_pill_bottle", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 250), col="red")
#text(x = 1.5, y = min(which(test.dat$ActivityName == "6._Med_Taking") + 650), "Pour_pill", cex = 0.5)
#abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 800), col="red")
text(x = 1.5, y = min(which(test.dat$ActivityName == "6._Med_Taking") + 375), "Pour_pill_return_bottle_and_take_pill", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "6._Med_Taking") + 500), col="red")
text(x = 1.5, y = min(which(test.dat$ActivityName == "6._Med_Taking") + 600), "Others", cex = 0.5)

abline(h = min(which(test.dat$ActivityName == "7._Med_Taking")), col="red")
text(x = 1.5, y = min(which(test.dat$ActivityName == "7._Med_Taking") + 225), "Pick_up_and_open_a_water_bottle_and_pill_bottle", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "7._Med_Taking") + 450), col="red")
text(x = 1.5, y = min(which(test.dat$ActivityName == "7._Med_Taking") + 550), "Pour_pill_return_bottle_and_take_pill", cex = 0.5)
abline(h = min(which(test.dat$ActivityName == "7._Med_Taking") + 650), col="red")
# text(x = 1.5, y = min(which(test.dat$ActivityName == "7._Med_Taking") + 1250), "Take_pill", cex = 0.5)
# abline(h = min(which(test.dat$ActivityName == "7._Med_Taking") + 1300), col="red")
text(x = 1.5, y = min(which(test.dat$ActivityName == "7._Med_Taking") + 800), "Others", cex = 0.5)
```


```{r}
## add label for trained activities
test.dat.patient.52$Label2 <- test.dat.patient.52$Label
test.dat.patient.52$Label2[c(
 min(which(test.dat$ActivityName == "4._Med_Taking")):
 min(which(test.dat$ActivityName == "4._Med_Taking")+ 700),
 min(which(test.dat$ActivityName == "5._Med_Taking")):
 min(which(test.dat$ActivityName == "5._Med_Taking")+ 250),
 min(which(test.dat$ActivityName == "6._Med_Taking")):
 min(which(test.dat$ActivityName == "6._Med_Taking")+ 250),
 min(which(test.dat$ActivityName == "7._Med_Taking")):
 min(which(test.dat$ActivityName == "7._Med_Taking")+ 450),
 min(which(test.dat$ActivityName == "8._Med_Taking")):
 min(which(test.dat$ActivityName == "8._Med_Taking")+ 400),
 min(which(test.dat$ActivityName == "10._Med_Taking")):
 min(which(test.dat$ActivityName == "10._Med_Taking")+ 500),
 min(which(test.dat$ActivityName == "11._Med_Taking")):
 min(which(test.dat$ActivityName == "11._Med_Taking")+ 300),
 min(which(test.dat$ActivityName == "12._Med_Taking")):
 min(which(test.dat$ActivityName == "12._Med_Taking")+ 300)
 )] <- "Pick_up_and_open_pill_bottle"

test.dat.patient.52$Label2[c(
 min(which(test.dat$ActivityName == "4._Med_Taking") + 701):
 min(which(test.dat$ActivityName == "4._Med_Taking") + 1150),
 min(which(test.dat$ActivityName == "5._Med_Taking") + 251):
 min(which(test.dat$ActivityName == "5._Med_Taking") + 500),
 min(which(test.dat$ActivityName == "6._Med_Taking") + 251):
 min(which(test.dat$ActivityName == "6._Med_Taking") + 500),
 min(which(test.dat$ActivityName == "7._Med_Taking") + 451):
 min(which(test.dat$ActivityName == "7._Med_Taking") + 650),
 min(which(test.dat$ActivityName == "8._Med_Taking") + 401):
 min(which(test.dat$ActivityName == "8._Med_Taking") + 650),
 min(which(test.dat$ActivityName == "10._Med_Taking") + 501):
 min(which(test.dat$ActivityName == "10._Med_Taking") + 800),
 min(which(test.dat$ActivityName == "11._Med_Taking") + 301):
 min(which(test.dat$ActivityName == "11._Med_Taking") + 650),
 min(which(test.dat$ActivityName == "12._Med_Taking") + 301):
 min(which(test.dat$ActivityName == "12._Med_Taking") + 400)
 )] <- "Pour_pill_return_bottle_and_take_pill"

temp <- data.frame(cbind(test.dat.patient.52$Label2, patient52_8_meds$Pred2, 
                         patient52_8_meds$Pred))
colnames(temp) <- c("Label","Pred","Pred_num")
temp <- temp[test.dat.patient.52$Label2 %in% c("Pick_up_and_open_pill_bottle","Pour_pill_return_bottle_and_take_pill"), ]

## determine number of med taking activities and their location in the data
train <- rle(as.character(temp$Label))
test <- rle(as.numeric(temp$Pred_num))
rle_diff <- diff(test$values)
Pick_up_and_open_pill_bottle_idx <- which(train$values == "Pick_up_and_open_pill_bottle")

## how many % of correct prediction needed to classify a correct prediction?
cut_off <- seq(0.50,0.7,0.05)
pred_res_acc_median <- c()
correct_med_pred <- c()
#true_label <-  c("Med-taking session","Not med-taking","Part of Med-taking, not a full session","Med-taking session","Med-taking session","Med-taking session","Part of Med-taking, not a full session","Med-taking session", "Med-taking session","Med-taking session","Part of Med-taking, not a full session","Part of Med-taking, not a full session","Med-taking session","Part of Med-taking, not a full session")
for (j in 1:length(cut_off)){
  ## determine the cut off for prediction length
  correct_pred_cut_off <- c()
  for(i in 1:length(Pick_up_and_open_pill_bottle_idx)){
    correct_pred_cut_off[i] <- cut_off[j] * sum(train$lengths[Pick_up_and_open_pill_bottle_idx][i] + train$lengths[Pick_up_and_open_pill_bottle_idx + 1][i])
  }
  correct_pred_cut_off_median <- median(correct_pred_cut_off)
  
  ## determine accuracy of the prediction
  pred_res <- c()
  for (i in which(rle_diff == 1)){
    if(test$values[i] == 1 & test$values[i+1] == 2){
      if(test$lengths[i] + test$lengths[i+1] > correct_pred_cut_off_median){
          pred_res <- c(pred_res,"Med-taking session")
        } else {pred_res <- c(pred_res,"Part of Med-taking, not a full session")}
    } else {pred_res <- c(pred_res,"Not med-taking")}
  }
  #pred_res_acc_median[j] <- round(sum(pred_res == true_label)/length(pred_res),2)
  #correct_med_pred[j] <- sum(which(pred_res == "Med-taking session") == which(true_label == "Med-taking session"))
  correct_med_pred[j] <- length(which(pred_res == "Med-taking session"))
}

data.frame(cut_off,correct_med_pred, med_session = 8)

## Calculating accuracy
Pick_up_and_open_pill_bottle_acc <- sum(as.character(temp$Label) %in% "Pick_up_and_open_pill_bottle" & as.character(temp$Pred) %in% "Pick_up_and_open_pill_bottle")/sum(as.character(temp$Label) %in% "Pick_up_and_open_pill_bottle")
Pour_pill_return_bottle_and_take_pill_acc <- sum(as.character(temp$Label) %in% "Pour_pill_return_bottle_and_take_pill" & as.character(temp$Pred) %in% "Pour_pill_return_bottle_and_take_pill")/sum(as.character(temp$Label) %in% "Pour_pill_return_bottle_and_take_pill")

## create 2x2 tables
obs_pick_pred_pick <- sum(as.character(temp$Label) %in% "Pick_up_and_open_pill_bottle" & as.character(temp$Pred) %in% "Pick_up_and_open_pill_bottle")
obs_pick_pred_others <- sum(as.character(temp$Label) %in% "Pick_up_and_open_pill_bottle" & !(as.character(temp$Pred) %in% "Pick_up_and_open_pill_bottle"))
obs_pour_pred_others <- sum(as.character(temp$Label) %in% "Pour_pill_return_bottle_and_take_pill" & !(as.character(temp$Pred) %in% "Pour_pill_return_bottle_and_take_pill"))
obs_pour_pred_pour <- sum(as.character(temp$Label) %in% "Pour_pill_return_bottle_and_take_pill" & as.character(temp$Pred) %in% "Pour_pill_return_bottle_and_take_pill")

## row = obs, col = pred
acc_mat <- matrix(c(obs_pick_pred_pick,obs_pick_pred_others,obs_pour_pred_others,obs_pour_pred_pour), byrow = TRUE, nrow = 2)
#acc_mat
```

The accuracy for predicting "pick up and open pill bottle" is `r round(Pick_up_and_open_pill_bottle_acc,4)` and the accuracy for predicting "pour pill, return bottle and take pill" is `r round(Pour_pill_return_bottle_and_take_pill_acc,4)`.

Another way that we determine accuracy is to determine whether the prediction is med-taking related or not. Based on this definition, we construct a confusion matrix below: 

```{r, calc_acc}
#length(test.dat.patient.52$Label)
#length(patient52_8_meds$Pred2)
temp2 <- data.frame(cbind(test.dat.patient.52$Label[1:length(patient52_8_meds$Pred2)], patient52_8_meds$Pred2))
temp2$True_label <- factor(ifelse(temp2$X1 %in% c("Open_Door","Turn_Key","Eat_From_Bag"), "Not Med Taking","Med Taking"))
temp2$Pred_label <- factor(ifelse(temp2$X2 %in% c("Wash_Hands","Look_around_in_bag_or_purse"), "Not Med Taking","Med Taking"))
conf_mat <- confusionMatrix(data = temp2$Pred_label, reference = temp2$True_label)
conf_mat$table
conf_mat$overall[1]
```

## Try movelet with patient 86

```{r}
#Load Data
# dat_86_88_89<-read.csv('/Users/quycao/Box/PipPenn/Data/Patients-86-88-89.csv',header = TRUE,stringsAsFactors = FALSE)
# dat_86 <- subset(dat_86_88_89, PatientID == 86)
# saveRDS(dat_86, file = "patient_86.rds")
dat <- readRDS(file = "/Users/quycao/Box/PipPenn/Data/patient_86.rds")
dat$Activitylabel<-match(dat$ActivityName,unique(dat$ActivityName))
#convert time series and reorder data by time
dat$timestamp<-substr(dat$activity_timestamp,12,23)
dat$time<-as.numeric(hms(dat$timestamp))
dat <- dat[sort.int(dat$time, index.return = TRUE)$ix, ]
dat$time<-dat$time-dat$time[1]

## Relabel names for wrist location
dat$Wrist_Location <- ifelse(dat$Wrist_Location =="right     ","right","left")

## remove duplicate left and right wrist to create balance data
dat$Wrist_Location2 <- ifelse(dat$Wrist_Location == "left", 0, 1)
keep_idx <- c()
diff_time <- diff(dat$time)
diff_wrist <- diff(dat$Wrist_Location2)

for (i in 1:length(diff_time)){
  if (diff_time[i] <= 0.01 & diff_wrist[i] != 0)
  {
    keep_idx = c(keep_idx, i, i + 1) 
  }
  i = i + 2
}
nodup_dat <- dat[keep_idx, ]
table(nodup_dat$Wrist_Location)

## extract 3 pcs for the left hand
vars_left <- nodup_dat[nodup_dat$Wrist_Location=="left",
                       c("accel_x_coord","accel_y_coord","accel_z_coord",
                        "rotate_x_coord","rotate_y_coord", "rotate_z_coord",
                        "gravity_x_coord","gravity_z_coord","gravity_y_coord",
                        "magneto_x_coord","magneto_y_coord","magneto_z_coord",
                        "attitude_x_coord","attitude_y_coord","attitude_z_coord")]
varsleft.pca <- prcomp(vars_left, center=TRUE, scale.=TRUE)
#summary(varsleft.pca)
pcs_left <- varsleft.pca$x[,1:3]

## extract 3 pcs for the right hand
vars_right <- nodup_dat[nodup_dat$Wrist_Location=="right",
                       c("accel_x_coord","accel_y_coord","accel_z_coord",
                        "rotate_x_coord","rotate_y_coord", "rotate_z_coord",
                        "gravity_x_coord","gravity_z_coord","gravity_y_coord",
                        "magneto_x_coord","magneto_y_coord","magneto_z_coord",
                        "attitude_x_coord","attitude_y_coord","attitude_z_coord")]
varsright.pca <- prcomp(vars_right, center=TRUE, scale.=TRUE)
#summary(varsright.pca)
pcs_right <- varsright.pca$x[,1:3]

pcs_combined <- cbind(pcs_left,pcs_right)
colnames(pcs_combined) <- c("PC1_left","PC2_left","PC3_left","PC1_right","PC2_right","PC3_right")

## combine data with Pcs
ActivityName <- nodup_dat$ActivityName[nodup_dat$Wrist_Location=="left"]
movelet.dat <- data.frame(pcs_combined, ActivityName)
movelet.dat$ActivityName <- gsub(" ", "_", movelet.dat$ActivityName)

## Reorder movelet into left hand then right hand for each activity
#movelet.dat <- movelet.dat[order(movelet.dat$ActivityName,movelet.dat$Wrist_Location),]

## create accel data 
patient.86 <- Acceleration_Create2(movelet.dat,subjectName="patient86",
                                   n_axes = 6,frequency=50) # 50 obs per second
## train pick up and open a pill bottle chapter
## 9._Med_Taking is about 18 seconds, about 900 observations, so 1 sec = 50 obs. 
from <- min(which(patient.86$Label == "9._Med_Taking")) + 100 ## 12:40:39 
to <- min(which(patient.86$Label == "9._Med_Taking")) + 300 ## 12:40:43
Ch.Pick_up_and_open_pill_bottle.patient86 <- Movelet_Create2(FROM = from ,TO = to, 
                                    DATA = patient.86, n_axes = 6,
                                    ChapName = "Pick_up_and_open_pill_bottle")
## train pour pill, return bottle and take pill chapter 
from <- min(which(patient.86$Label == "9._Med_Taking")) + 300 ## 12:40:43
to <- min(which(patient.86$Label == "9._Med_Taking")) + 500 ## 12:11:47
Ch.Pour_pill_return_bottle_and_take_pill.patient86 <- Movelet_Create2(FROM = from ,TO = to, 
                                    DATA = patient.86, n_axes = 6,
                                    ChapName = "Pour_pill_return_bottle_and_take_pill")
## train Wash_Hands chapter
from <- min(which(patient.86$Label == "Wash_Hands"))
to <- max(which(patient.86$Label == "Wash_Hands"))
Ch.Wash_Hands.patient86 <- Movelet_Create2(FROM = from ,TO = to,
                                    DATA = patient.86, n_axes = 6,
                                    ChapName = "Wash_Hands")
## train Look_around_in_bag_or_purse chapter
from <- min(which(patient.86$Label == "Look_around_in_bag_or_purse"))
to <- max(which(patient.86$Label == "Look_around_in_bag_or_purse"))
Ch.Look_around_in_bag_or_purse.patient86 <- Movelet_Create2(FROM = from ,TO = to,
                                    DATA = patient.86, n_axes = 6,
                                    ChapName = "Look_around_in_bag_or_purse")
## test data
test.dat <- subset(movelet.dat, ActivityName %in% c("Turn_Key","Open_Door","Eat_From_Bag","6._Med_Taking","7._Med_Taking","8._Med_Taking",
  "10._Med_Taking","11._Med_Taking","12._Med_Taking"))
test.dat.patient.86 <- Acceleration_Create2(test.dat,subjectName="patient86",n_axes = 6,frequency=50) 
train.label=c("Pick_up_and_open_pill_bottle","Pour_pill_return_bottle_and_take_pill","Wash_Hands","Look_around_in_bag_or_purse")
```

```{r, eval = FALSE}
#expand the prediction activity labels to include all trained chapters
pred <- Movelet_Pred2(test.dat.patient.86, Act.Names=train.label, vote=TRUE)
# Save it
#saveRDS(pred, file = "patient86_6pcs_both_separated_wrists_pred.rds")
saveRDS(pred, file = "patient86_6_meds.rds")
```

```{r}
# load it
patient86_6_meds <- readRDS(file = "patient86_6_meds.rds")
patient86_6_meds$Pred2 <- recode(patient86_6_meds$Pred, `1`="Pick_up_and_open_pill_bottle", `2`="Pour_pill_return_bottle_and_take_pill", `3`="Wash_Hands", `4`="Look_around_in_bag_or_purse")
```

```{r}
## add label for trained activities
test.dat.patient.86$Label2 <- test.dat.patient.86$Label
test.dat.patient.86$Label2[c(
 min(which(test.dat$ActivityName == "6._Med_Taking")+ 100):
 min(which(test.dat$ActivityName == "6._Med_Taking")+ 250),
 min(which(test.dat$ActivityName == "7._Med_Taking")+ 50):
 min(which(test.dat$ActivityName == "7._Med_Taking")+ 300),
 min(which(test.dat$ActivityName == "8._Med_Taking")+ 150):
 min(which(test.dat$ActivityName == "8._Med_Taking")+ 400),
 min(which(test.dat$ActivityName == "10._Med_Taking")+ 100):
 min(which(test.dat$ActivityName == "10._Med_Taking")+ 300),
 min(which(test.dat$ActivityName == "11._Med_Taking")+ 50):
 min(which(test.dat$ActivityName == "11._Med_Taking")+ 250),
 min(which(test.dat$ActivityName == "12._Med_Taking")+ 50):
 min(which(test.dat$ActivityName == "12._Med_Taking")+ 250)
 )] <- "Pick_up_and_open_pill_bottle"

test.dat.patient.86$Label2[c(
 min(which(test.dat$ActivityName == "6._Med_Taking") + 251):
 min(which(test.dat$ActivityName == "6._Med_Taking") + 500),
 min(which(test.dat$ActivityName == "7._Med_Taking") + 301):
 min(which(test.dat$ActivityName == "7._Med_Taking") + 450),
 min(which(test.dat$ActivityName == "8._Med_Taking") + 401):
 min(which(test.dat$ActivityName == "8._Med_Taking") + 500),
 min(which(test.dat$ActivityName == "10._Med_Taking") + 301):
 min(which(test.dat$ActivityName == "10._Med_Taking") + 750),
 min(which(test.dat$ActivityName == "11._Med_Taking") + 251):
 min(which(test.dat$ActivityName == "11._Med_Taking") + 600),
 min(which(test.dat$ActivityName == "12._Med_Taking") + 251):
 min(which(test.dat$ActivityName == "12._Med_Taking") + 400)
 )] <- "Pour_pill_return_bottle_and_take_pill"

temp <- data.frame(cbind(test.dat.patient.86$Label2, patient86_6_meds$Pred2, 
                         patient86_6_meds$Pred))
colnames(temp) <- c("Label","Pred","Pred_num")
temp <- temp[test.dat.patient.86$Label2 %in% c("Pick_up_and_open_pill_bottle","Pour_pill_return_bottle_and_take_pill"), ]

## determine number of med taking activities and their location in the data
train <- rle(as.character(temp$Label))
test <- rle(as.numeric(temp$Pred_num))
rle_diff <- diff(test$values)
Pick_up_and_open_pill_bottle_idx <- which(train$values == "Pick_up_and_open_pill_bottle")

## how many % of correct prediction needed to classify a correct prediction?
cut_off <- seq(0.50,0.7,0.05)
pred_res_acc_median <- c()
correct_med_pred <- c()
#true_label <-  c("Other activities","Med-taking session","Other activities","Med-taking session","Not Med-taking session","Other activities","Med-taking session","Other activities","Med-taking session","Other activities")
for (j in 1:length(cut_off)){
  ## determine the cut off for prediction length
  correct_pred_cut_off <- c()
  for(i in 1:length(Pick_up_and_open_pill_bottle_idx)){
    correct_pred_cut_off[i] <- cut_off[j] * sum(train$lengths[Pick_up_and_open_pill_bottle_idx][i] + train$lengths[Pick_up_and_open_pill_bottle_idx + 1][i])
  }
  correct_pred_cut_off_median <- median(correct_pred_cut_off)
  
  ## determine accuracy of the prediction
  pred_res <- c()
  for (i in which(rle_diff == 1)){
    if(test$values[i] == 1 & test$values[i+1] == 2){
      if(test$lengths[i] + test$lengths[i+1] > correct_pred_cut_off_median){
          pred_res <- c(pred_res,"Med-taking session")
        } else {pred_res <- c(pred_res,"Part of med-taking session")}
    } else {pred_res <- c(pred_res,"Not med-taking session")}
  }
  #pred_res_acc_median[j] <- round(sum(pred_res == true_label)/length(pred_res),2)
  #correct_med_pred[j] <- sum(which(pred_res == "Med-taking session") == which(true_label == "Med-taking session"))
  correct_med_pred[j] <- length(which(pred_res == "Med-taking session"))
}

data.frame(cut_off,correct_med_pred, med_session = 6)

## Calculating accuracy
Pick_up_and_open_pill_bottle_acc <- sum(as.character(temp$Label) %in% "Pick_up_and_open_pill_bottle" & as.character(temp$Pred) %in% "Pick_up_and_open_pill_bottle")/sum(as.character(temp$Label) %in% "Pick_up_and_open_pill_bottle")
Pour_pill_return_bottle_and_take_pill_acc <- sum(as.character(temp$Label) %in% "Pour_pill_return_bottle_and_take_pill" & as.character(temp$Pred) %in% "Pour_pill_return_bottle_and_take_pill")/sum(as.character(temp$Label) %in% "Pour_pill_return_bottle_and_take_pill")

## create 2x2 tables
obs_pick_pred_pick <- sum(as.character(temp$Label) %in% "Pick_up_and_open_pill_bottle" & as.character(temp$Pred) %in% "Pick_up_and_open_pill_bottle")
obs_pick_pred_others <- sum(as.character(temp$Label) %in% "Pick_up_and_open_pill_bottle" & !(as.character(temp$Pred) %in% "Pick_up_and_open_pill_bottle"))
obs_pour_pred_others <- sum(as.character(temp$Label) %in% "Pour_pill_return_bottle_and_take_pill" & !(as.character(temp$Pred) %in% "Pour_pill_return_bottle_and_take_pill"))
obs_pour_pred_pour <- sum(as.character(temp$Label) %in% "Pour_pill_return_bottle_and_take_pill" & as.character(temp$Pred) %in% "Pour_pill_return_bottle_and_take_pill")

## row = obs, col = pred
acc_mat <- matrix(c(obs_pick_pred_pick,obs_pick_pred_others,obs_pour_pred_others,obs_pour_pred_pour), byrow = TRUE, nrow = 2)
#acc_mat
```

For this result, movelet couldn't detect the first two medication taking sessions. Specifically, the length of prediction for med taking 1 is (72,57) and for med taking 2 is (69,107,192).

```{r}
test$lengths[1:8]
test$values[1:8]
```

The accuracy for predicting "pick up and open pill bottle" is `r round(Pick_up_and_open_pill_bottle_acc,4)` and the accuracy for predicting "pour pill, return bottle and take pill" is `r round(Pour_pill_return_bottle_and_take_pill_acc,4)`.

Another way that we determine accuracy is to determine whether the prediction is med-taking related or not. Based on this definition, we construct a confusion matrix below: 

```{r, calc_acc_patient_86}
#length(test.dat.patient.86$Label)
#length(patient86_6_meds$Pred2)
temp2 <- data.frame(cbind(test.dat.patient.86$Label[1:length(patient86_6_meds$Pred2)], patient86_6_meds$Pred2))
temp2$True_label <- factor(ifelse(temp2$X1 %in% c("Open_Door","Turn_Key","Eat_From_Bag"), "Not Med Taking","Med Taking"))
temp2$Pred_label <- factor(ifelse(temp2$X2 %in% c("Wash_Hands","Look_around_in_bag_or_purse"), "Not Med Taking","Med Taking"))
conf_mat <- confusionMatrix(data = temp2$Pred_label, reference = temp2$True_label)
conf_mat$table
conf_mat$overall[1]
```

## Try movelet with patient 88

```{r}
#Load Data
# dat_86_88_89<-read.csv('/Users/quycao/Box/PipPenn/Data/Patients-86-88-89.csv',header = TRUE,stringsAsFactors = FALSE)
# dat_88 <- subset(dat_86_88_89, PatientID == 88)
# saveRDS(dat_88, file = "patient_88.rds")
dat <- readRDS(file = "/Users/quycao/Box/PipPenn/Data/patient_88.rds")
dat$Activitylabel<-match(dat$ActivityName,unique(dat$ActivityName))
#convert time series and reorder data by time
dat$timestamp<-substr(dat$activity_timestamp,12,23)
dat$time<-as.numeric(hms(dat$timestamp))
dat <- dat[sort.int(dat$time, index.return = TRUE)$ix, ]
dat$time<-dat$time-dat$time[1]

## Relabel names for wrist location
dat$Wrist_Location <- ifelse(dat$Wrist_Location =="right     ","right","left")

## remove duplicate left and right wrist to create balance data
dat$Wrist_Location2 <- ifelse(dat$Wrist_Location == "left", 0, 1)
keep_idx <- c()
diff_time <- diff(dat$time)
diff_wrist <- diff(dat$Wrist_Location2)

for (i in 1:length(diff_time)){
  if (diff_time[i] <= 0.01 & diff_wrist[i] != 0)
  {
    keep_idx = c(keep_idx, i, i + 1) 
  }
  i = i + 2
}
nodup_dat <- dat[keep_idx, ]
table(nodup_dat$Wrist_Location)

## extract 3 pcs for the left hand
vars_left <- nodup_dat[nodup_dat$Wrist_Location=="left",
                       c("accel_x_coord","accel_y_coord","accel_z_coord",
                        "rotate_x_coord","rotate_y_coord", "rotate_z_coord",
                        "gravity_x_coord","gravity_z_coord","gravity_y_coord",
                        "magneto_x_coord","magneto_y_coord","magneto_z_coord",
                        "attitude_x_coord","attitude_y_coord","attitude_z_coord")]
varsleft.pca <- prcomp(vars_left, center=TRUE, scale.=TRUE)
#summary(varsleft.pca)
pcs_left <- varsleft.pca$x[,1:3]

## extract 3 pcs for the right hand
vars_right <- nodup_dat[nodup_dat$Wrist_Location=="right",
                       c("accel_x_coord","accel_y_coord","accel_z_coord",
                        "rotate_x_coord","rotate_y_coord", "rotate_z_coord",
                        "gravity_x_coord","gravity_z_coord","gravity_y_coord",
                        "magneto_x_coord","magneto_y_coord","magneto_z_coord",
                        "attitude_x_coord","attitude_y_coord","attitude_z_coord")]
varsright.pca <- prcomp(vars_right, center=TRUE, scale.=TRUE)
#summary(varsright.pca)
pcs_right <- varsright.pca$x[,1:3]

pcs_combined <- cbind(pcs_left,pcs_right)
colnames(pcs_combined) <- c("PC1_left","PC2_left","PC3_left","PC1_right","PC2_right","PC3_right")

## combine data with Pcs
ActivityName <- nodup_dat$ActivityName[nodup_dat$Wrist_Location=="left"]
movelet.dat <- data.frame(pcs_combined, ActivityName)
movelet.dat$ActivityName <- gsub(" ", "_", movelet.dat$ActivityName)

## create accel data 
patient.88 <- Acceleration_Create2(movelet.dat,subjectName="patient88",
                                   n_axes = 6,frequency=50) # 50 obs per second
## train pick up and open a pill bottle chapter
## 1 sec = 50 obs. 
from <- min(which(patient.88$Label == "9._Med_Taking")) + 200
to <- min(which(patient.88$Label == "9._Med_Taking")) + 350 
Ch.Pick_up_and_open_pill_bottle.patient88 <- Movelet_Create2(FROM = from ,TO = to, 
                                    DATA = patient.88, n_axes = 6,
                                    ChapName = "Pick_up_and_open_pill_bottle")
## train pour pill, return bottle and take pill chapter 
from <- min(which(patient.88$Label == "9._Med_Taking")) + 350
to <- min(which(patient.88$Label == "9._Med_Taking")) + 500 
Ch.Pour_pill_return_bottle_and_take_pill.patient88 <- Movelet_Create2(FROM = from ,TO = to, 
                                    DATA = patient.88, n_axes = 6,
                                    ChapName = "Pour_pill_return_bottle_and_take_pill")
## train Wash_Hands chapter
from <- min(which(patient.88$Label == "Wash_Hands"))
to <- max(which(patient.88$Label == "Wash_Hands"))
Ch.Wash_Hands.patient88 <- Movelet_Create2(FROM = from ,TO = to,
                                    DATA = patient.88, n_axes = 6,
                                    ChapName = "Wash_Hands")
## train Look_around_in_bag_or_purse chapter
from <- min(which(patient.88$Label == "Look_around_in_bag_or_purse"))
to <- max(which(patient.88$Label == "Look_around_in_bag_or_purse"))
Ch.Look_around_in_bag_or_purse.patient88 <- Movelet_Create2(FROM = from ,TO = to,
                                    DATA = patient.88, n_axes = 6,
                                    ChapName = "Look_around_in_bag_or_purse")
## test data
test.dat <- subset(movelet.dat, ActivityName %in% c("Turn_Key","Open_Door","Eat_From_Bag","4._Med_Taking","5._Med_Taking","6._Med_Taking","7._Med_Taking","8._Med_Taking","10._Med_Taking","11._Med_Taking","12._Med_Taking"))
test.dat.patient.88 <- Acceleration_Create2(test.dat,subjectName="patient88",n_axes = 6,frequency=50) 
train.label=c("Pick_up_and_open_pill_bottle","Pour_pill_return_bottle_and_take_pill","Wash_Hands","Look_around_in_bag_or_purse")
```

```{r, eval = FALSE}
#expand the prediction activity labels to include all trained chapters
pred <- Movelet_Pred2(test.dat.patient.88, Act.Names=train.label, vote=TRUE)
# Save it
#saveRDS(pred, file = "patient86_6pcs_both_separated_wrists_pred.rds")
saveRDS(pred, file = "patient88_8_meds.rds")
```

```{r}
# load it
patient88_8_meds <- readRDS(file = "patient88_8_meds.rds")
patient88_8_meds$Pred2 <- recode(patient88_8_meds$Pred, `1`="Pick_up_and_open_pill_bottle", `2`="Pour_pill_return_bottle_and_take_pill", `3`="Wash_Hands", `4`="Look_around_in_bag_or_purse")
```

```{r, eval = FALSE}
## add label for trained activities
test.dat.patient.88$Label2 <- test.dat.patient.88$Label
test.dat.patient.88$Label2[c(
 min(which(test.dat$ActivityName == "4._Med_Taking")+ 50):
 min(which(test.dat$ActivityName == "4._Med_Taking")+ 200),
 min(which(test.dat$ActivityName == "5._Med_Taking")+ 50):
 min(which(test.dat$ActivityName == "5._Med_Taking")+ 200),
 min(which(test.dat$ActivityName == "6._Med_Taking")+ 100):
 min(which(test.dat$ActivityName == "6._Med_Taking")+ 250),
 min(which(test.dat$ActivityName == "7._Med_Taking")+ 200):
 min(which(test.dat$ActivityName == "7._Med_Taking")+ 350),
 min(which(test.dat$ActivityName == "8._Med_Taking")+ 150):
 min(which(test.dat$ActivityName == "8._Med_Taking")+ 300),
 min(which(test.dat$ActivityName == "10._Med_Taking")+ 150):
 min(which(test.dat$ActivityName == "10._Med_Taking")+ 350),
 min(which(test.dat$ActivityName == "11._Med_Taking")+ 100):
 min(which(test.dat$ActivityName == "11._Med_Taking")+ 300),
 min(which(test.dat$ActivityName == "12._Med_Taking")+ 200):
 min(which(test.dat$ActivityName == "12._Med_Taking")+ 350)
 )] <- "Pick_up_and_open_pill_bottle"

test.dat.patient.88$Label2[c(
 min(which(test.dat$ActivityName == "4._Med_Taking")+ 201):
 min(which(test.dat$ActivityName == "4._Med_Taking")+ 450),
 min(which(test.dat$ActivityName == "5._Med_Taking")+ 201):
 min(which(test.dat$ActivityName == "5._Med_Taking")+ 350),
 min(which(test.dat$ActivityName == "6._Med_Taking") + 251):
 min(which(test.dat$ActivityName == "6._Med_Taking") + 400),
 min(which(test.dat$ActivityName == "7._Med_Taking") + 351):
 min(which(test.dat$ActivityName == "7._Med_Taking") + 500),
 min(which(test.dat$ActivityName == "8._Med_Taking") + 301):
 min(which(test.dat$ActivityName == "8._Med_Taking") + 400),
 min(which(test.dat$ActivityName == "10._Med_Taking") + 351):
 min(which(test.dat$ActivityName == "10._Med_Taking") + 550),
 min(which(test.dat$ActivityName == "11._Med_Taking") + 301):
 min(which(test.dat$ActivityName == "11._Med_Taking") + 500),
 min(which(test.dat$ActivityName == "12._Med_Taking") + 351):
 min(which(test.dat$ActivityName == "12._Med_Taking") + 500)
 )] <- "Pour_pill_return_bottle_and_take_pill"

temp <- data.frame(cbind(test.dat.patient.88$Label2, patient88_8_meds$Pred2, 
                         patient88_8_meds$Pred))
colnames(temp) <- c("Label","Pred","Pred_num")
temp <- temp[test.dat.patient.88$Label2 %in% c("Pick_up_and_open_pill_bottle","Pour_pill_return_bottle_and_take_pill"), ]

## determine number of med taking activities and their location in the data
train <- rle(as.character(temp$Label))
test <- rle(as.numeric(temp$Pred_num))
rle_diff <- diff(test$values)
Pick_up_and_open_pill_bottle_idx <- which(train$values == "Pick_up_and_open_pill_bottle")

## how many % of correct prediction needed to classify a correct prediction?
cut_off <- seq(0.50,0.7,0.05)
pred_res_acc_median <- c()
correct_med_pred <- c()
#true_label <-  c("Other activities","Med-taking session","Other activities","Med-taking session","Not Med-taking session","Other activities","Med-taking session","Other activities","Med-taking session","Other activities")
for (j in 1:length(cut_off)){
  ## determine the cut off for prediction length
  correct_pred_cut_off <- c()
  for(i in 1:length(Pick_up_and_open_pill_bottle_idx)){
    correct_pred_cut_off[i] <- cut_off[j] * sum(train$lengths[Pick_up_and_open_pill_bottle_idx][i] + train$lengths[Pick_up_and_open_pill_bottle_idx + 1][i])
  }
  correct_pred_cut_off_median <- median(correct_pred_cut_off)
  
  ## determine accuracy of the prediction
  pred_res <- c()
  for (i in which(rle_diff == 1)){
    if(test$values[i] == 1 & test$values[i+1] == 2){
      if(test$lengths[i] + test$lengths[i+1] > correct_pred_cut_off_median){
          pred_res <- c(pred_res,"Med-taking session")
        } else {pred_res <- c(pred_res,"Part of med-taking session")}
    } else {pred_res <- c(pred_res,"Not med-taking session")}
  }
  #pred_res_acc_median[j] <- round(sum(pred_res == true_label)/length(pred_res),2)
  #correct_med_pred[j] <- sum(which(pred_res == "Med-taking session") == which(true_label == "Med-taking session"))
  correct_med_pred[j] <- length(which(pred_res == "Med-taking session"))
}

data.frame(cut_off,correct_med_pred, med_session = 8)

## Calculating accuracy
Pick_up_and_open_pill_bottle_acc <- sum(as.character(temp$Label) %in% "Pick_up_and_open_pill_bottle" & as.character(temp$Pred) %in% "Pick_up_and_open_pill_bottle")/sum(as.character(temp$Label) %in% "Pick_up_and_open_pill_bottle")
Pour_pill_return_bottle_and_take_pill_acc <- sum(as.character(temp$Label) %in% "Pour_pill_return_bottle_and_take_pill" & as.character(temp$Pred) %in% "Pour_pill_return_bottle_and_take_pill")/sum(as.character(temp$Label) %in% "Pour_pill_return_bottle_and_take_pill")

## create 2x2 tables
obs_pick_pred_pick <- sum(as.character(temp$Label) %in% "Pick_up_and_open_pill_bottle" & as.character(temp$Pred) %in% "Pick_up_and_open_pill_bottle")
obs_pick_pred_others <- sum(as.character(temp$Label) %in% "Pick_up_and_open_pill_bottle" & !(as.character(temp$Pred) %in% "Pick_up_and_open_pill_bottle"))
obs_pour_pred_others <- sum(as.character(temp$Label) %in% "Pour_pill_return_bottle_and_take_pill" & !(as.character(temp$Pred) %in% "Pour_pill_return_bottle_and_take_pill"))
obs_pour_pred_pour <- sum(as.character(temp$Label) %in% "Pour_pill_return_bottle_and_take_pill" & as.character(temp$Pred) %in% "Pour_pill_return_bottle_and_take_pill")

## row = obs, col = pred
acc_mat <- matrix(c(obs_pick_pred_pick,obs_pick_pred_others,obs_pour_pred_others,obs_pour_pred_pour), byrow = TRUE, nrow = 2)
#acc_mat
```

```{r, calc_acc_patient_88}
#length(test.dat.patient.86$Label)
#length(patient86_6_meds$Pred2)
temp2 <- data.frame(cbind(test.dat.patient.88$Label[1:length(patient88_8_meds$Pred2)], patient88_8_meds$Pred2))
temp2$True_label <- factor(ifelse(temp2$X1 %in% c("Open_Door","Turn_Key","Eat_From_Bag"), "Not Med Taking","Med Taking"))
temp2$Pred_label <- factor(ifelse(temp2$X2 %in% c("Wash_Hands","Look_around_in_bag_or_purse"), "Not Med Taking","Med Taking"))
conf_mat <- confusionMatrix(data = temp2$Pred_label, reference = temp2$True_label)
conf_mat$table
conf_mat$overall[1]
```


