---
title: 'Movelet: Output for Paper'
author: "Virgilio Gonzenbach"
date: "10/7/2021"
output:
  html_document: 
    toc: true
    toc_float: true
    theme: spacelab
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center",
                      message = FALSE, 
                      warning = FALSE,
                      fig.width = 10,
                      fig.height = 7,
                      dpi=300,
                      fig.path = here::here('figures/'))
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r load}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggpubr)
library(ggsci)
library(flextable)
source("Code/functions.R")
source("Code/summary.R")

metrics_df <- read.csv('metrics_df.csv')
metrics_df_all_n <- read.csv('metrics_df_all_n.csv')
```

## Comparisons

### Number of PCs

```{r npc_boxplots}
metrics_df %>% 
  filter(pca == 'bothhands') %>% 
  mutate(npc = as.factor(npc)) %>% 
  group_by(patient, smooth, npc) %>% 
  select(Accuracy, Precision, F1.score, Sensitivity, Specificity) %>% 
  summarize_all(mean) %>% 
  ungroup() %>% 
  pivot_longer(-c(npc, patient, smooth), names_to = "Metric") %>% 
  ggplot(aes(x=Metric, y=value, color=npc)) + 
  geom_boxplot() + 
  facet_wrap(~smooth) + 
  theme_bw() + theme(plot.title = element_text(hjust = 0.5)) +
  scale_color_lancet()
ggsave('figures/npc_boxplot.png', dpi=300)
```

## Dominant Hand vs Both Hands (w. npc=3)

```{r pca_boxplots}
metrics_df_for_plot = metrics_df %>% 
  filter(npc == 3 | npc == 6) %>% 
  mutate(npc = as.factor(npc), patient=as.factor(patient)) %>% 
  group_by(patient, smooth, pca) %>% 
  select(Accuracy, Precision, F1.score, Sensitivity, Specificity) %>% 
  summarize_all(mean) %>% 
  ungroup() 

metrics_df_for_plot %>% 
  pivot_longer(-c(pca, patient, smooth), names_to = "Metric") %>% 
  mutate(pca = recode(.$pca, `bothhands` = "Both Hands", `dominanthand` = "Dominant Hand")) %>% 
  ggplot(aes(x=Metric, y=value, color=pca)) + 
  geom_boxplot() + 
  facet_wrap(~smooth) + 
  theme_bw() + theme(plot.title = element_text(hjust = 0.5)) +
  scale_color_lancet() + 
  labs(color='PCA')
  
```

Testing differences

```{r}
bothhands = metrics_df_for_plot %>% 
  filter(smooth=='Post-Smoothing', pca=='bothhands') %>% 
  select(where(is.numeric))

domhand = metrics_df_for_plot %>% 
  filter(smooth=='Post-Smoothing', pca=='dominanthand') %>% 
  select(where(is.numeric))

metrics_df_for_plot %>% 
  filter(smooth=='Post-Smoothing') %>% 
  group_split(pca)

res = seq_along(bothhands) %>% lapply(function(i) t.test(domhand[,i], bothhands[,i]))
names(res) = colnames(domhand)
res
```

## Both Hands NPC=3 per hand

### Training 1 med session

```{r}
metrics_df_long = metrics_df %>% filter(pca == 'bothhands', npc==3) %>% group_by(patient, smooth) %>% select(Accuracy, Precision, F1.score, Sensitivity, Specificity) %>% summarize_all(mean) %>% pivot_longer(-c(patient, smooth), names_to = "Metric")

metrics_df_long %>% ggplot(aes(x=Metric, y = value, color=Metric)) + geom_jitter() + geom_boxplot(alpha=0) + facet_wrap(~smooth) + 
  theme_bw() + ggtitle("Summary metrics for Movelet prediction (1 session training)") + theme(plot.title = element_text(hjust = 0.5)) +
  scale_color_d3()
```

### Metrics across sessions

```{r results='asis'}

# Prepare table with smoothing
table1 = metrics_df %>% filter(smooth=="Pre-Smoothing", pca == 'bothhands', npc==3) %>% group_by(session) %>% select(Accuracy, Precision, F1.score, Sensitivity, Specificity) %>% summarize_all(mean)

# Prepare table without smoothing
table2 = metrics_df %>% filter(smooth=="Post-Smoothing", pca == 'bothhands', npc==3) %>% group_by(session) %>% select(Accuracy, Precision, F1.score, Sensitivity, Specificity) %>% summarize_all(mean) %>% as.data.frame()

# Join tables
tables = cbind(table1, table2[, -1]) %>% round(2)
colnames(tables)[2:11] = paste0(colnames(tables)[2:11], rep(c(".T", ".F"), each = 5))
headers = data.frame(col_keys = colnames(tables), 
                     from = c("Session", rep(c("Pre-Smoothing", "Post-Smoothing"), each=5)),
                     names = c("Session", colnames(cbind(table1[-1], table2[, -1])))
                     )
# Print table as flextable
tables %>% flextable::flextable() %>% 
  set_header_df(mapping = headers, key = "col_keys") %>% 
  merge_h(part="header") %>% 
  merge_v(part="header") %>% 
  theme_vanilla() %>% 
  width(width = 27, unit = "in") %>% 
  align(align="center", part="all") %>% 
  vline(part="header")
  
```

### Metrics across training modes

```{r}
metrics_df_all_n %>% 
  filter(pca == 'bothhands', npc==3) %>% 
  group_by(patient, n_train, smooth) %>% 
  select(Accuracy, Precision, F1.score, Sensitivity, Specificity) %>% 
  summarize_all(mean) %>% 
  pivot_longer(-c(patient, n_train, smooth),  names_to = "Metric") %>% 
  ggplot(aes(x=n_train, y = value, color=as.factor(n_train))) + 
  geom_jitter() + facet_grid(smooth~Metric) +  geom_boxplot(alpha=0) + 
  theme_bw() + ggtitle("Summary metrics for Movelet prediction (n session training)") + 
  theme(plot.title = element_text(hjust = 0.5)) + guides(color=guide_legend(title="N trained med sessions")) + xlab("Train N") +
  scale_color_lancet() 
  
```

## Both Hands NPC=4

### Training 1 med session

```{r}
metrics_df_long = metrics_df %>% filter(pca == 'bothhands', npc==4) %>% group_by(patient, smooth) %>% select(Accuracy, Precision, F1.score, Sensitivity, Specificity) %>% summarize_all(mean) %>% pivot_longer(-c(patient, smooth), names_to = "Metric")

metrics_df_long %>% ggplot(aes(x=Metric, y = value, color=Metric)) + geom_jitter() + geom_boxplot(alpha=0) + facet_wrap(~smooth) + 
  theme_bw() + ggtitle("Summary metrics for Movelet prediction (1 session training)") + theme(plot.title = element_text(hjust = 0.5)) +
  scale_color_d3()
```

### Metrics across sessions

```{r results='asis'}

# Prepare table with smoothing
table1 = metrics_df %>% filter(smooth=="Pre-Smoothing", pca == 'bothhands', npc==4) %>% group_by(session) %>% select(Accuracy, Precision, F1.score, Sensitivity, Specificity) %>% summarize_all(mean)

# Prepare table without smoothing
table2 = metrics_df %>% filter(smooth=="Post-Smoothing", pca == 'bothhands', npc==4) %>% group_by(session) %>% select(Accuracy, Precision, F1.score, Sensitivity, Specificity) %>% summarize_all(mean) %>% as.data.frame()

# Join tables
tables = cbind(table1, table2[, -1]) %>% round(2)
colnames(tables)[2:11] = paste0(colnames(tables)[2:11], rep(c(".T", ".F"), each = 5))
headers = data.frame(col_keys = colnames(tables), 
                     from = c("Session", rep(c("Pre-Smoothing", "Post-Smoothing"), each=5)),
                     names = c("Session", colnames(cbind(table1[-1], table2[, -1])))
                     )
# Print table as flextable
tables %>% flextable::flextable() %>% 
  set_header_df(mapping = headers, key = "col_keys") %>% 
  merge_h(part="header") %>% 
  merge_v(part="header") %>% 
  theme_vanilla() %>% 
  width(width = 27, unit = "in") %>% 
  align(align="center", part="all") %>% 
  vline(part="header")
  
```

### Metrics across traning modes

```{r}
metrics_df_all_n %>% 
  filter(pca == 'bothhands', npc==4) %>% 
  group_by(patient, n_train, smooth) %>% 
  select(Accuracy, Precision, F1.score, Sensitivity, Specificity) %>% 
  summarize_all(mean) %>% 
  pivot_longer(-c(patient, n_train, smooth),  names_to = "Metric") %>% 
  ggplot(aes(x=n_train, y = value, color=as.factor(n_train))) + 
  geom_jitter() + facet_grid(smooth~Metric) +  geom_boxplot(alpha=0) + 
  theme_bw() + ggtitle("Summary metrics for Movelet prediction (n session training)") + 
  theme(plot.title = element_text(hjust = 0.5)) + guides(color=guide_legend(title="N trained med sessions")) + xlab("Train N") +
  scale_color_lancet() 
  
```

## Both Hands NPC=5

### Training 1 med session

```{r}
metrics_df_long = metrics_df %>% filter(pca == 'bothhands', npc==5) %>% group_by(patient, smooth) %>% select(Accuracy, Precision, F1.score, Sensitivity, Specificity) %>% summarize_all(mean) %>% pivot_longer(-c(patient, smooth), names_to = "Metric")

metrics_df_long %>% ggplot(aes(x=Metric, y = value, color=Metric)) + geom_jitter() + geom_boxplot(alpha=0) + facet_wrap(~smooth) + 
  theme_bw() + ggtitle("Summary metrics for Movelet prediction (1 session training)") + theme(plot.title = element_text(hjust = 0.5)) +
  scale_color_d3()
```

### Metrics across sessions

```{r results='asis'}

# Prepare table with smoothing
table1 = metrics_df %>% filter(smooth=="Pre-Smoothing", pca == 'bothhands', npc==5) %>% group_by(session) %>% select(Accuracy, Precision, F1.score, Sensitivity, Specificity) %>% summarize_all(mean)

# Prepare table without smoothing
table2 = metrics_df %>% filter(smooth=="Post-Smoothing", pca == 'bothhands', npc==5) %>% group_by(session) %>% select(Accuracy, Precision, F1.score, Sensitivity, Specificity) %>% summarize_all(mean) %>% as.data.frame()

# Join tables
tables = cbind(table1, table2[, -1]) %>% round(2)
colnames(tables)[2:11] = paste0(colnames(tables)[2:11], rep(c(".T", ".F"), each = 5))
headers = data.frame(col_keys = colnames(tables), 
                     from = c("Session", rep(c("Pre-Smoothing", "Post-Smoothing"), each=5)),
                     names = c("Session", colnames(cbind(table1[-1], table2[, -1])))
                     )
# Print table as flextable
tables %>% flextable::flextable() %>% 
  set_header_df(mapping = headers, key = "col_keys") %>% 
  merge_h(part="header") %>% 
  merge_v(part="header") %>% 
  theme_vanilla() %>% 
  width(width = 27, unit = "in") %>% 
  align(align="center", part="all") %>% 
  vline(part="header")
  
```

### Metrics across traning modes

```{r}
metrics_df_all_n %>% 
  filter(pca == 'bothhands', npc==5) %>% 
  group_by(patient, n_train, smooth) %>% 
  select(Accuracy, Precision, F1.score, Sensitivity, Specificity) %>% 
  summarize_all(mean) %>% 
  pivot_longer(-c(patient, n_train, smooth),  names_to = "Metric") %>% 
  ggplot(aes(x=n_train, y = value, color=as.factor(n_train))) + 
  geom_jitter() + facet_grid(smooth~Metric) +  geom_boxplot(alpha=0) + 
  theme_bw() + ggtitle("Summary metrics for Movelet prediction (n session training)") + 
  theme(plot.title = element_text(hjust = 0.5)) + guides(color=guide_legend(title="N trained med sessions")) + xlab("Train N") +
  scale_color_lancet() 
  
```


## Dominant Hand

### Training 1 med session

```{r}
metrics_df_long = metrics_df %>% filter(pca == 'dominanthand') %>% group_by(patient, smooth) %>% select(Accuracy, Precision, F1.score, Sensitivity, Specificity) %>% summarize_all(mean) %>% pivot_longer(-c(patient, smooth), names_to = "Metric")

metrics_df_long %>% ggplot(aes(x=Metric, y = value, color=Metric)) + geom_jitter() + geom_boxplot(alpha=0) + facet_wrap(~smooth) + 
  theme_bw() + ggtitle("Summary metrics for Movelet prediction (1 session training)") + theme(plot.title = element_text(hjust = 0.5)) +
  scale_color_d3()
```

### Metrics across sessions

```{r results='asis'}

# Prepare table with smoothing
table1 = metrics_df %>% filter(smooth=="Pre-Smoothing", pca == 'dominanthand') %>% group_by(session) %>% select(Accuracy, Precision, F1.score, Sensitivity, Specificity) %>% summarize_all(mean)

# Prepare table without smoothing
table2 = metrics_df %>% filter(smooth=="Post-Smoothing", pca == 'dominanthand') %>% group_by(session) %>% select(Accuracy, Precision, F1.score, Sensitivity, Specificity) %>% summarize_all(mean) %>% as.data.frame()

# Join tables
tables = cbind(table1, table2[, -1]) %>% round(2)
colnames(tables)[2:11] = paste0(colnames(tables)[2:11], rep(c(".T", ".F"), each = 5))
headers = data.frame(col_keys = colnames(tables), 
                     from = c("Session", rep(c("Pre-Smoothing", "Post-Smoothing"), each=5)),
                     names = c("Session", colnames(cbind(table1[-1], table2[, -1])))
                     )
# Print table as flextable
tables %>% flextable::flextable() %>% 
  set_header_df(mapping = headers, key = "col_keys") %>% 
  merge_h(part="header") %>% 
  merge_v(part="header") %>% 
  theme_vanilla() %>% 
  width(width = 27, unit = "in") %>% 
  align(align="center", part="all") %>% 
  vline(part="header")
  
```

### Metrics across traning modes

```{r}
metrics_df_all_n %>% 
  filter(pca == 'dominanthand') %>% 
  group_by(patient, n_train, smooth) %>% 
  select(Accuracy, Precision, F1.score, Sensitivity, Specificity) %>% 
  summarize_all(mean) %>% 
  pivot_longer(-c(patient, n_train, smooth),  names_to = "Metric") %>% 
  ggplot(aes(x=n_train, y = value, color=as.factor(n_train))) + 
  geom_jitter() + facet_grid(smooth~Metric) +  geom_boxplot(alpha=0) + 
  theme_bw() + ggtitle("Summary metrics for Movelet prediction (n session training)") + 
  theme(plot.title = element_text(hjust = 0.5)) + guides(color=guide_legend(title="N trained med sessions")) + xlab("Train N") +
  scale_color_lancet() 
  
```
